---
title: "DO Drug-Na&iuml;ve Demographic Data Summarize"
author: "Michael C. Saul (michael.saul [at] jax.org)"
output: workflowr::wflow_html
---

# Background

## Motivation

### Purpose of analysis

This initial script exists to summarize the demographic data of a number of mice used in this study.

# Analysis

## Setup

### R libraries

Calling R libraries necessary for this analysis.

```{r libraries}
library("readxl")
library("lubridate")
```

# Data Import

## Importing data

### Importing basic mouse demographic data

Importing and cleaning up basic demographic data (note: original version of file was named `DO Mice.xlsx` with spaces included, but file name was changed to add underscores on 2020-05-01).

The md5 checksum of the input `DO_Mice.xlsx` file is: ``r tools::md5sum("./data/raw/DO_Mice.xlsx")``.

```{r demodata_import}
DO_demodata = as.data.frame(read_excel("./data/raw/DO_Mice.xlsx"), stringsAsFactors = FALSE)
colnames(DO_demodata) = c("Mouse_ID", "Strain", "DOB", "Sex")
row.names(DO_demodata) = as.character(DO_demodata$Mouse_ID)
DO_demodata = DO_demodata[,-1]
DO_demodata$DOB = mdy(DO_demodata$DOB)
```

### Summarizing demographic data as data frame for future use

```{r demodata_summarize}
# Saving demodata
saveRDS(DO_demodata,"./data/DO_demographic_data_df.RDS",compress="xz")
```

The md5 checksum of the output file (`DO_demographic_data_df.RDS`) is: ``r tools::md5sum("./data/DO_demographic_data_df.RDS")``.

These are the measures used, and they are already summarized as a data frame.

Measure Name    | Measure Description
----------------|-----------------------------------------------------
`Strain`        | Mouse strain used in in study
`DOB`           | Mouse date of birth
`Sex`           | Sex of mouse

### Document Control

This document was prepared using RMarkdown in RStudio and imported into workflowr on 2020-05-01.

(file was formerly saved as [DO_demographic_data_summarize.html](DO_demographic_data_summarize.html))
