---
title: "DO Drug-Na&iuml;ve Novelty Behavior Summarization"
author: "Michael C. Saul (michael.saul [at] jax.org)"
output: workflowr::wflow_html
---

# Background

## Motivation

### Purpose of analysis

This analysis is to summarize the novelty response behavioral data.

# Analysis

## Setup

### R libraries

Calling R libraries necessary for this analysis.

```{r libraries}
library("readxl")
library("ggplot2")
library("lubridate")
```

# Data Import

## Importing data

### Importing basic mouse demographic data

Importing basic demographic data.

The md5 checksum of the input file (`DO_demographic_data_df.RDS`) is: ``r tools::md5sum("./data/DO_demographic_data_df.RDS")``.

```{r demodata_import}
DO_demodata = readRDS("./data/DO_demographic_data_df.RDS")
```

These are the measures used, and they are already summarized as a data frame.

Measure Name    | Measure Description
----------------|-----------------------------------------------------
`Strain`        | Mouse strain used in in study
`DOB`           | Mouse date of birth
`Sex`           | Sex of mouse

### Importing and summarizing holeboard data

Importing DO holeboard data as cleaned up, properly data typed, and deduplicated in the `DO_holeboard_summarize.Rmd` script.

The md5 checksum of the input file (`DO_holeboard_summarized.RDS`) is: ``r tools::md5sum("./data/DO_holeboard_summarized.RDS")``.

```{r holeboarddata_import}
DO_holeboard_raw = readRDS("./data/DO_holeboard_summarized.RDS")

DO_holeboard_data_cols = c("Distance_Traveled","Time_Ambulatory_sec","Ambulatory_Count",
                           "Time_Stereotypic_sec","Stereotypic_Count","Time_Resting_sec",
                           "Jump_Count","Time_Jumping_sec","Average_Velocity","Ambulatory_Episodes",
                           "Latency_To_First_Hole_sec","Novel_Entries","Repeat_Entries",
                           "Total_Entries","Avg_Novel_Total_IRT")

DO_holeboard = DO_holeboard_raw[,DO_holeboard_data_cols]
rm(list = c("DO_holeboard_raw","DO_holeboard_data_cols"))

# Saving holeboard data
saveRDS(DO_holeboard,"./data/DO_holeboard_data_df.RDS",compress="xz")
```

The md5 checksum of the output file (`DO_holeboard_data_df.RDS`) is: ``r tools::md5sum("./data/DO_holeboard_data_df.RDS")``

These are the measures used, and they are already summarized as a data frame.

Measure Name                | Measure Description
----------------------------|----------------------------------------------------------
`Distance_Traveled`         | Distance travelled in the holeboard apparatus (cm)
`Time_Ambulatory_sec`       | Time spent traveling in the holeboard apparatus (sec)
`Ambulatory_Count`          | Count of ambulatory activity
`Time_Stereotypic_sec`      | Time spent engaged in stereotypic behavior (sec)
`Stereotypic_Count`         | Count of sterotypic behavior
`Time_Resting_sec`          | Time spent resting in the apparatus (sec)
`Jump_Count`                | Count of jumps
`Time_Jumping_sec`          | Time spent jumping (sec)
`Average_Velocity`          | Average speed the mouse was moving (unsure of units)
`Ambulatory_Episodes`       | Count of episodes moving
`Latency_To_First_Hole_sec` | Time in seconds until first hole dip (1200 = no dip)
`Novel_Entries`             | Count of entries into novel holes
`Repeat_Entries`            | Count of entries into holes previously entered
`Total_Entries`             | Count of total hole board entries
`Avg_Novel_Total_IRT`       | An inter-task measure of time for novel entries

The holeboard trials are each 20 minutes (1200 seconds) long.

### Importing light-dark data

Importing and cleaning up DO light-dark data (note: original version of file was named `DO LightDark modified.xlsx` with spaces included, but file name was changed to add underscores on 2020-05-01).

The md5 checksum of the input file (`DO_LightDark_modified.xlsx`) is: ``r tools::md5sum("./data/raw/DO_LightDark_modified.xlsx")``

```{r lightdarkdata_import}
DO_lightdark_raw = as.data.frame(read_excel("./data/raw/DO_LightDark_modified.xlsx"),
                                 stringsAsFactors = FALSE)
row.names(DO_lightdark_raw) = as.character(DO_lightdark_raw[,"Subject"])
DO_lightdark_raw = DO_lightdark_raw[,(-1 * which(colnames(DO_lightdark_raw) == "Subject"))]
colnames(DO_lightdark_raw) = gsub(" ", "_", colnames(DO_lightdark_raw))
```

### Summarizing light-dark data

Zone 1 is light; zone 2 is dark.

Deriving the following measures into a data frame:

Measure Name            | Measure Description
------------------------|---------------------------------------------------------------
`Light_Dist`            | Distance traveled in light compartment
`Dark_Dist`             | Distance traveled in dark compartment
`Total_Dist`            | Total distance traveled in both compartments
`P_Light_Dist`          | Proportion of distance traveled in light compartment
`P_Dark_Dist`           | Proportion of distance traveled in dark compartment
`Light_Sec`             | Seconds spent ambulating in light compartment
`Dark_Sec`              | Seconds spent ambulating in dark compartment
`Total_Sec`             | Total seconds spent ambulating in both compartments
`P_Light_Sec`           | Proportion of ambulating seconds spent in light compartment
`P_Dark_Sec`            | Proportion of ambulating seconds spent in dark compartment
`Transitions`           | Total transitions between light and dark
`P_Stereotypic_Light`   | Proportion of stereotypic time in light
`Sec_Stereotypic_Dark`  | Number of seconds spent in stereotypic behavior in dark
`Light_Resting_Sec`     | Total resting time in the light
`Dark_Resting_Sec`      | Total resting time in the dark
`Light_Amb_Counts`      | Ambulatory counts in light
`Dark_Amb_Counts`       | Ambulatory counts in dark
`Total_Amb_Counts`      | Ambulatory counts total
`P_Amb_Counts_Light`    | Proportion of ambulatory counts in light
`P_Amb_Counts_Dark`     | Proportion of ambulatory counts in dark
`Light_Duration`        | Duration spent in light
`Dark_Duration`         | Duration spent in dark
`Total_Duration`        | Total duration spent in light/dark box
`P_Duration_Light`      | Proportion of duration spent in light
`P_Duration_Dark`       | Proportion of duration spent in dark

To integrate:
LD_pct_time_in_light

Distances are centimeters.

```{r lightdarkdata_summarize}
# Using initial columns for information
DO_lightdark = rbind(DO_lightdark_raw[,1:19])
DO_lightdark_noinfo = which(colSums(is.na(DO_lightdark)) == nrow(DO_lightdark))
DO_lightdark = DO_lightdark[,(-1 * DO_lightdark_noinfo)]
rm(list = c("DO_lightdark_noinfo"))

# Calculating distance-related measures
Light_Dist_cols = colnames(DO_lightdark_raw)[grep("^Ambulatory_Distance_Bin_\\d{1,2}_Zone_1$", colnames(DO_lightdark_raw))]
Dark_Dist_cols = colnames(DO_lightdark_raw)[grep("^Ambulatory_Distance_Bin_\\d{1,2}_Zone_2$", colnames(DO_lightdark_raw))]
Total_Dist_cols = colnames(DO_lightdark_raw)[grep("^Ambulatory_Distance_Bin_\\d{1,2}$", colnames(DO_lightdark_raw))]
Light_Stereotypic_Time_cols = colnames(DO_lightdark_raw)[grep("^Stereotypic_Time_Bin_\\d{1,2}_Zone_1$", colnames(DO_lightdark_raw))]
Dark_Stereotypic_Time_cols = colnames(DO_lightdark_raw)[grep("^Stereotypic_Time_Bin_\\d{1,2}_Zone_2$", colnames(DO_lightdark_raw))]
Light_Resting_Time_cols = colnames(DO_lightdark_raw)[grep("^Resting_Time_Bin_\\d{1,2}_Zone_1$", colnames(DO_lightdark_raw))]
Dark_Resting_Time_cols = colnames(DO_lightdark_raw)[grep("^Resting_Time_Bin_\\d{1,2}_Zone_2$", colnames(DO_lightdark_raw))]

DO_lightdark$Light_Dist = rowSums(as.matrix(DO_lightdark_raw[,Light_Dist_cols]))
DO_lightdark$Dark_Dist = rowSums(as.matrix(DO_lightdark_raw[,Dark_Dist_cols]))
DO_lightdark$Total_Dist = rowSums(as.matrix(DO_lightdark_raw[,Total_Dist_cols]))
DO_lightdark$P_Light_Dist = DO_lightdark$Light_Dist / DO_lightdark$Total_Dist
DO_lightdark$P_Dark_Dist = DO_lightdark$Dark_Dist / DO_lightdark$Total_Dist

# Calculating time-related measures
Light_Sec_cols = colnames(DO_lightdark_raw)[grep("^Ambulatory_Time_Bin_\\d{1,2}_Zone_1$", colnames(DO_lightdark_raw))]
Dark_Sec_cols = colnames(DO_lightdark_raw)[grep("^Ambulatory_Time_Bin_\\d{1,2}_Zone_2$", colnames(DO_lightdark_raw))]
Total_Sec_cols = colnames(DO_lightdark_raw)[grep("^Ambulatory_Time_Bin_\\d{1,2}$", colnames(DO_lightdark_raw))]
DO_lightdark$Light_Sec = rowSums(as.matrix(DO_lightdark_raw[,Light_Sec_cols]))
DO_lightdark$Dark_Sec = rowSums(as.matrix(DO_lightdark_raw[,Dark_Sec_cols]))
DO_lightdark$Total_Sec = rowSums(as.matrix(DO_lightdark_raw[,Total_Sec_cols]))
DO_lightdark$P_Light_Sec = DO_lightdark$Light_Sec / DO_lightdark$Total_Sec
DO_lightdark$P_Dark_Sec = DO_lightdark$Dark_Sec / DO_lightdark$Total_Sec
DO_lightdark$P_Stereotypic_Light = rowSums(as.matrix(DO_lightdark_raw[,Light_Stereotypic_Time_cols])) / (rowSums(as.matrix(DO_lightdark_raw[,Light_Stereotypic_Time_cols])) + rowSums(as.matrix(DO_lightdark_raw[,Dark_Stereotypic_Time_cols])))
DO_lightdark$Sec_Stereotypic_Dark = rowSums(as.matrix(DO_lightdark_raw[,Dark_Stereotypic_Time_cols]))
DO_lightdark$Light_Resting_Sec = rowSums(as.matrix(DO_lightdark_raw[,Light_Resting_Time_cols]))
DO_lightdark$Dark_Resting_Sec = rowSums(as.matrix(DO_lightdark_raw[,Dark_Resting_Time_cols]))

# Calculating transitions
Transitions_cols = colnames(DO_lightdark_raw)[grep("^Zone_Entries_Bin_\\d{1,2}$", colnames(DO_lightdark_raw))]
DO_lightdark$Transitions = rowSums(as.matrix(DO_lightdark_raw[,Transitions_cols]))

# Calculating ambulatory counts
Light_Counts_cols = colnames(DO_lightdark_raw)[grep("^Ambulatory_Counts_Bin_\\d{1,2}_Zone_1$", colnames(DO_lightdark_raw))]
Dark_Counts_cols = colnames(DO_lightdark_raw)[grep("^Ambulatory_Counts_Bin_\\d{1,2}_Zone_2$", colnames(DO_lightdark_raw))]
Total_Counts_cols = colnames(DO_lightdark_raw)[grep("^Ambulatory_Counts_Bin_\\d{1,2}$", colnames(DO_lightdark_raw))]
DO_lightdark$Light_Amb_Counts = rowSums(as.matrix(DO_lightdark_raw[,Light_Counts_cols]))
DO_lightdark$Dark_Amb_Counts = rowSums(as.matrix(DO_lightdark_raw[,Dark_Counts_cols]))
DO_lightdark$Total_Amb_Counts = rowSums(as.matrix(DO_lightdark_raw[,Total_Counts_cols]))
DO_lightdark$P_Amb_Counts_Light = DO_lightdark$Light_Amb_Counts / DO_lightdark$Total_Amb_Counts
DO_lightdark$P_Amb_Counts_Dark = DO_lightdark$Dark_Amb_Counts / DO_lightdark$Total_Amb_Counts

# Calculating duration
Light_Duration_cols = colnames(DO_lightdark_raw)[grep("^Duration_Bin_\\d{1,2}_Zone_1$", colnames(DO_lightdark_raw))]
Dark_Duration_cols = colnames(DO_lightdark_raw)[grep("^Duration_Bin_\\d{1,2}_Zone_2$", colnames(DO_lightdark_raw))]
Total_Duration_cols = colnames(DO_lightdark_raw)[grep("^Duration_Bin_\\d{1,2}$", colnames(DO_lightdark_raw))]
DO_lightdark$Light_Duration = rowSums(as.matrix(DO_lightdark_raw[,Light_Duration_cols]))
DO_lightdark$Dark_Duration = rowSums(as.matrix(DO_lightdark_raw[,Dark_Duration_cols]))
DO_lightdark$Total_Duration = rowSums(as.matrix(DO_lightdark_raw[,Total_Duration_cols]))
DO_lightdark$P_Duration_Light = DO_lightdark$Light_Duration / DO_lightdark$Total_Duration
DO_lightdark$P_Duration_Dark = DO_lightdark$Dark_Duration / DO_lightdark$Total_Duration

# Removing helper vectors
rm(list = ls()[grep("cols$",ls())])

# Saving raw data
saveRDS(DO_lightdark_raw, "./data/raw/DO_lightdark_raw.RDS", compress = "xz")
rm(list = c("DO_lightdark_raw"))

# Saving light-dark data
saveRDS(DO_lightdark,"./data/DO_lightdark_data_df.RDS",compress="xz")
```

The md5 checksum of the output file (`DO_lightdark_raw.RDS`) is: ``r tools::md5sum("./data/raw/DO_lightdark_raw.RDS")``

The md5 checksum of the output file (`DO_lightdark_data_df.RDS`) is: ``r tools::md5sum("./data/DO_lightdark_data_df.RDS")``

### Importing open field data

(note: original version of file was named `DO Open field modified.xlsx` with spaces included, but file name was changed to add underscores on 2020-05-01)

The md5 checksum of the input file (`DO_Open_field_modified.xlsx`) is: ``r tools::md5sum("./data/raw/DO_Open_field_modified.xlsx")``.

```{r openfielddata_import}
DO_openfield_raw = as.data.frame(read_excel("./data/raw/DO_Open_field_modified.xlsx"),
                                 stringsAsFactors = FALSE)
row.names(DO_openfield_raw) = as.character(DO_openfield_raw$Subject)
DO_openfield_raw = DO_openfield_raw[,(-1 * which(colnames(DO_openfield_raw) == "Subject"))]
colnames(DO_openfield_raw) = gsub(" ", "_", colnames(DO_openfield_raw))
```

### Summarizing open field data

Deriving the following measures into a data frame:

Measure Name            | Measure Description
------------------------|-----------------------------------------------------
`Perimeter_Dist`        | Total distance traveled in the perimeter
`Corner_Dist`           | Total distance traveled in the corner
`Center_Dist`           | Total distance traveled in the center
`Total_Dist`            | Total distance traveled in open field
`P_Perimeter_Dist`      | Proportion of distance spent in perimeter
`P_Corner_Dist`         | Proportion of distance spent in corner
`P_Center_Dist`         | Proportion of distance spent in center
`Perimeter_Time`        | Seconds spent ambulating in perimeter
`Corner_Time`           | Seconds spent ambulating in corner
`Center_Time`           | Seconds spent ambulating in center
`Total_Time`            | Total seconds spent ambulating in the open field
`Rest_Time_Corner`      | Seconds spent resting in the corner
`Rest_Time_Center`      | Seconds spent resting in the center
`Rest_Time_Perimeter`   | Seconds spent resting in the perimeter
`Rest_Time_Total`       | Total seconds spent resting in the open field
`P_Corner_Rest_Time`    | Proportion of rest time spent in corner
`P_Center_Rest_Time`    | Proportion of rest time spent in center
`P_Perimeter_Rest_Time` | Proportion of rest time spent in perimeter
`P_Perimeter_Time`      | Proportion of seconds spent ambulating in perimeter
`P_Corner_Time`         | Proportion of seconds spent ambulating in corner
`P_Center_Time`         | Proportion of seconds spent ambulating in center
`Ambulatory_Counts`     | Number of ambulatory counts
`Dist_Slope`            | Slope of open field distance
`Dist_Last_Five`        | Distance travelled in last 5 minutes
`Dist_First_Five`       | Distance travelled in first 5 minutes

```{r openfielddata_summarize}
# Using initial columns for information
DO_openfield = DO_openfield_raw[,1:19]
DO_openfield_noinfo = which(colSums(is.na(DO_openfield)) == nrow(DO_openfield))
DO_openfield = DO_openfield[,(-1 * DO_openfield_noinfo)]
rm(list = c("DO_openfield_noinfo"))

# Calculating open field distances
Perimeter_Dist_cols = colnames(DO_openfield_raw)[grep("^Ambulatory_Distance_Bin_\\d{1,2}_Zone_\\w{3,6}_Perimeter$", colnames(DO_openfield_raw))]
Corner_Dist_cols = colnames(DO_openfield_raw)[grep("^Ambulatory_Distance_Bin_\\d{1,2}_Zone_\\w{3,6}_\\w{4,5}_Corner$", colnames(DO_openfield_raw))]
Center_Dist_cols = colnames(DO_openfield_raw)[grep("^Ambulatory_Distance_Bin_\\d{1,2}_Zone_Center$", colnames(DO_openfield_raw))]
Total_Dist_cols = colnames(DO_openfield_raw)[grep("^Ambulatory_Distance_Bin_\\d{1,2}$", colnames(DO_openfield_raw))]

Total_Dist_slopevals = as.numeric(gsub("Ambulatory_Distance_Bin_","",Total_Dist_cols))

DO_openfield$Perimeter_Dist = rowSums(as.matrix(DO_openfield_raw[,Perimeter_Dist_cols]))
DO_openfield$Corner_Dist = rowSums(as.matrix(DO_openfield_raw[,Corner_Dist_cols]))
DO_openfield$Center_Dist = rowSums(as.matrix(DO_openfield_raw[,Center_Dist_cols]))
DO_openfield$Total_Dist = rowSums(as.matrix(DO_openfield_raw[,Total_Dist_cols]))
DO_openfield$P_Perimeter_Dist = DO_openfield$Perimeter_Dist / DO_openfield$Total_Dist
DO_openfield$P_Corner_Dist = DO_openfield$Corner_Dist / DO_openfield$Total_Dist
DO_openfield$P_Center_Dist = DO_openfield$Center_Dist / DO_openfield$Total_Dist
DO_openfield$Dist_Slope = rep(NA, times = nrow(DO_openfield))
for (i in row.names(DO_openfield)) {
  DO_lm_i = summary(lm(as.numeric(DO_openfield_raw[i,Total_Dist_cols]) ~ Total_Dist_slopevals))
  DO_openfield[i,"Dist_Slope"] = DO_lm_i$coefficients["Total_Dist_slopevals","Estimate"]
}
DO_openfield$Dist_Last_Five = DO_openfield_raw[row.names(DO_openfield),"Ambulatory_Distance_Bin_12"]
DO_openfield$Dist_First_Five = DO_openfield_raw[row.names(DO_openfield),"Ambulatory_Distance_Bin_1"]

# Calculating open field times
Perimeter_Time_cols = colnames(DO_openfield_raw)[grep("^Ambulatory_Time_Bin_\\d{1,2}_Zone_\\w{3,6}_Perimeter$", colnames(DO_openfield_raw))]
Corner_Time_cols = colnames(DO_openfield_raw)[grep("^Ambulatory_Time_Bin_\\d{1,2}_Zone_\\w{3,6}_\\w{4,5}_Corner$", colnames(DO_openfield_raw))]
Center_Time_cols = colnames(DO_openfield_raw)[grep("^Ambulatory_Time_Bin_\\d{1,2}_Zone_Center$", colnames(DO_openfield_raw))]
Total_Time_cols = colnames(DO_openfield_raw)[grep("^Ambulatory_Time_Bin_\\d{1,2}$", colnames(DO_openfield_raw))]
DO_openfield$Perimeter_Time = rowSums(as.matrix(DO_openfield_raw[,Perimeter_Time_cols]))
DO_openfield$Corner_Time = rowSums(as.matrix(DO_openfield_raw[,Corner_Time_cols]))
DO_openfield$Center_Time = rowSums(as.matrix(DO_openfield_raw[,Center_Time_cols]))
DO_openfield$Total_Time = rowSums(as.matrix(DO_openfield_raw[,Total_Time_cols]))
DO_openfield$P_Perimeter_Time = DO_openfield$Perimeter_Time / DO_openfield$Total_Time
DO_openfield$P_Corner_Time = DO_openfield$Corner_Time / DO_openfield$Total_Time
DO_openfield$P_Center_Time = DO_openfield$Center_Time / DO_openfield$Total_Time

# Calculating open field rest times
Perimeter_Rest_Time_cols = colnames(DO_openfield_raw)[grep("^Resting_Time_Bin_\\d{1,2}_Zone_\\w{3,6}_Perimeter$", colnames(DO_openfield_raw))]
Corner_Rest_Time_cols = colnames(DO_openfield_raw)[grep("^Resting_Time_Bin_\\d{1,2}_Zone_\\w{3,6}_\\w{4,5}_Corner$", colnames(DO_openfield_raw))]
Center_Rest_Time_cols = colnames(DO_openfield_raw)[grep("^Resting_Time_Bin_\\d{1,2}_Zone_Center$", colnames(DO_openfield_raw))]
Total_Rest_Time_cols = colnames(DO_openfield_raw)[grep("^Resting_Time_Bin_\\d{1,2}$", colnames(DO_openfield_raw))]
DO_openfield$Rest_Time_Perimeter = rowSums(as.matrix(DO_openfield_raw[,Perimeter_Rest_Time_cols]))
DO_openfield$Rest_Time_Corner = rowSums(as.matrix(DO_openfield_raw[,Corner_Rest_Time_cols]))
DO_openfield$Rest_Time_Center = rowSums(as.matrix(DO_openfield_raw[,Center_Rest_Time_cols]))
DO_openfield$Rest_Time_Total = rowSums(as.matrix(DO_openfield_raw[,Total_Rest_Time_cols]))
DO_openfield$P_Perimeter_Rest_Time = DO_openfield$Rest_Time_Perimeter / DO_openfield$Rest_Time_Total
DO_openfield$P_Corner_Rest_Time = DO_openfield$Rest_Time_Corner / DO_openfield$Rest_Time_Total
DO_openfield$P_Center_Rest_Time = DO_openfield$Rest_Time_Center / DO_openfield$Rest_Time_Total

# Calculating ambulatory counts
Ambulatory_Counts_cols = colnames(DO_openfield_raw)[grep("^Ambulatory_Counts_Bin_\\d{1,2}$", colnames(DO_openfield_raw))]
DO_openfield$Ambulatory_Counts = rowSums(as.matrix(DO_openfield_raw[,Ambulatory_Counts_cols]))

# Removing helper vectors
rm(list = ls()[grep("cols$",ls())])

# Saving raw data
saveRDS(DO_openfield_raw, "./data/raw/DO_openfield_raw.RDS", compress = "xz")
rm(list = c("DO_openfield_raw"))

# Saving open field data
saveRDS(DO_openfield,"./data/DO_openfield_data_df.RDS",compress="xz")
```

The md5 checksum of the output file (`DO_openfield_raw.RDS`) is: ``r tools::md5sum("./data/raw/DO_openfield_raw.RDS")``.

The md5 checksum of the output file (`DO_openfield_data_df.RDS`) is: ``r tools::md5sum("./data/DO_openfield_data_df.RDS")``.

### Importing novel place preference data

The novel place preference behavioral paradigm contains the following phases:

1) Habituation: the animal spends 5 minutes in the grey zone
2) Exposure: the animal is exposed to the non-novel side for 20 minutes
3) Rest: the animal spends 5 minutes in the grey zone
4) Test: the animal spends 10-20 minutes with access to all three zones

In these tests, the animals had a 20-minute exposure to all three zones, but the data are summarized at 10 minutes to be compatible with later iterations of the paradigm, which had a 10 minute novelty test phase.

(note: original version of file was named `DO NPP 2_multivariate_file.xlsx` with spaces included, but file name was changed to add underscores on 2020-05-01)

The md5 checksum of the input file (`DO_NPP_2_multivariate_file.xlsx`) is: ``r tools::md5sum("./data/raw/DO_NPP_2_multivariate_file.xlsx")``.

```{r novelplacepreference_import}
DO_novelplace_raw = as.data.frame(read_excel("./data/raw/DO_NPP_2_multivariate_file.xlsx"),
                                  stringsAsFactors = FALSE)
```

### Summarizing novel place preference data

Deriving the following measures into a data frame:

Measure Name                              | Measure Description
------------------------------------------|----------------------------------------------------------------------------------------
`Box`                                     | Box ID used for the animal
`ExposureSide`                            | Zone of the apparatus used for the exposure (WHITE or BLACK)
`ZoneTime_WhiteVsBlack_Total`             | Time spent in test zone relative to exposure zone during full test
`ZoneTime_GreyWhiteBlack_Total`           | Time spent in test zone relative to exposure and grey zones during full test
`Grey_Time_First_Ten`                     | Time spent in grey zone during first ten minutes of test phase
`White_Time_First_Ten`                    | Time spent in white zone during first ten minutes of test phase
`Black_Time_First_Ten`                    | Time spent in black zone during first ten minutes of test phase
`ZoneTime_WhiteVsBlack_Total_FirstTen`    | Time spent in test zone relative to exposure zone during first 10 minutes
`ZoneTime_GreyWhiteBlack_Total_FirstTen`  | Time spent in test zone relative to exposure and grey zones during first 10 minutes


Note that the newer data use 10-minute NPP data instead of 20-minute.

```{r novelplacepreference_process}
# Using initial columns for information
DO_novelplace = DO_novelplace_raw[,1:12]
DO_novelplace_noinfo = which(colSums(is.na(DO_novelplace)) == nrow(DO_novelplace))
DO_novelplace = DO_novelplace[,(-1 * DO_novelplace_noinfo)]
rm(list = c("DO_novelplace_noinfo"))
colnames(DO_novelplace) = gsub("^Exposure - ","",colnames(DO_novelplace))
colnames(DO_novelplace) = gsub(" ","_",colnames(DO_novelplace))
colnames(DO_novelplace) = gsub("\\)","",colnames(DO_novelplace))
colnames(DO_novelplace) = gsub("\\(","",colnames(DO_novelplace))
DO_novelplace$ExposureSide = gsub("^Novelty_Preference_EXPOSURE_","",DO_novelplace$MEDState_Notation_Program_Name)
DO_novelplace$ZoneTime_WhiteVsBlack_Total = DO_novelplace_raw[,"NoveltyPreference - ZoneTime_WhiteVsBlack_Total"]
DO_novelplace$ZoneTime_GreyWhiteBlack_Total = DO_novelplace_raw[,"NoveltyPreference - ZoneTime_GreyWhiteBlack_Total"]

NPP_White_zonetime_cols = colnames(DO_novelplace_raw)[grep("^Test - ZoneTime_WhiteZone_Block\\d{2}$",colnames(DO_novelplace_raw))]
names(NPP_White_zonetime_cols) = gsub("^Test - ZoneTime_WhiteZone_Block(\\d{2})$","\\1",NPP_White_zonetime_cols)
NPP_White_zonetime_cols = NPP_White_zonetime_cols[which(as.numeric(names(NPP_White_zonetime_cols)) %in% 1:10)]
DO_novelplace$White_Time_First_Ten = rowSums(as.matrix(DO_novelplace_raw[,NPP_White_zonetime_cols]))

NPP_Black_zonetime_cols = colnames(DO_novelplace_raw)[grep("^Test - ZoneTime_BlackZone_Block\\d{2}$",colnames(DO_novelplace_raw))]
names(NPP_Black_zonetime_cols) = gsub("^Test - ZoneTime_BlackZone_Block(\\d{2})$","\\1",NPP_Black_zonetime_cols)
NPP_Black_zonetime_cols = NPP_Black_zonetime_cols[which(as.numeric(names(NPP_Black_zonetime_cols)) %in% 1:10)]
DO_novelplace$Black_Time_First_Ten = rowSums(as.matrix(DO_novelplace_raw[,NPP_Black_zonetime_cols]))

NPP_Grey_zonetime_cols = colnames(DO_novelplace_raw)[grep("^Test - ZoneTime_GreyZone_Block\\d{2}$",colnames(DO_novelplace_raw))]
names(NPP_Grey_zonetime_cols) = gsub("^Test - ZoneTime_GreyZone_Block(\\d{2})$","\\1",NPP_Grey_zonetime_cols)
NPP_Grey_zonetime_cols = NPP_Grey_zonetime_cols[which(as.numeric(names(NPP_Grey_zonetime_cols)) %in% 1:10)]
DO_novelplace$Grey_Time_First_Ten = rowSums(as.matrix(DO_novelplace_raw[,NPP_Grey_zonetime_cols]))

DO_novelplace$ZoneTime_WhiteVsBlack_Total_FirstTen = ifelse(DO_novelplace$ExposureSide == "WHITE",
                                                            DO_novelplace$Black_Time_First_Ten / (DO_novelplace$Black_Time_First_Ten + 
                                                                                                    DO_novelplace$White_Time_First_Ten),
                                                            DO_novelplace$White_Time_First_Ten / (DO_novelplace$Black_Time_First_Ten + 
                                                                                                    DO_novelplace$White_Time_First_Ten))
DO_novelplace$ZoneTime_GreyWhiteBlack_Total_FirstTen = ifelse(DO_novelplace$ExposureSide == "WHITE",
                                                              DO_novelplace$Black_Time_First_Ten / (DO_novelplace$Black_Time_First_Ten + 
                                                                                                      DO_novelplace$Grey_Time_First_Ten  + 
                                                                                                      DO_novelplace$White_Time_First_Ten),
                                                              DO_novelplace$White_Time_First_Ten / (DO_novelplace$Black_Time_First_Ten + 
                                                                                                      DO_novelplace$Grey_Time_First_Ten + 
                                                                                                      DO_novelplace$White_Time_First_Ten))
row.names(DO_novelplace) = DO_novelplace$Subject

# Removing helper vectors
rm(list = ls()[grep("cols$",ls())])

# Saving raw data
saveRDS(DO_novelplace_raw, "./data/raw/DO_novelplace_raw.RDS", compress = "xz")
rm(list = c("DO_novelplace_raw"))

# Saving open field data
saveRDS(DO_novelplace,"./data/DO_novelplace_data_df.RDS",compress="xz")
```

The md5 checksum of the output file (`DO_novelplace_raw.RDS`) is: ``r tools::md5sum("./data/raw/DO_novelplace_raw.RDS")``.

The md5 checksum of the output file (`DO_novelplace_data_df.RDS`) is: ``r tools::md5sum("./data/DO_novelplace_data_df.RDS")``.

### Document Control

This document was prepared using RMarkdown in RStudio and imported into workflowr on 2020-05-01.

(file was formerly saved as [DO_drug_naive_behavior_data_summarize.html](DO_drug_naive_behavior_data_summarize.html))
