---
title: "DO Drug-Na&iuml;ve eQTL Summarization"
author: "Michael C. Saul (michael.saul [at] jax.org)"
output: workflowr::wflow_html
---

# Background

## Motivation

### Purpose of analysis

This script is used to summarize eQTL data. Each gene is summarized and an overall dataset threshold is derived from 1,000 permutations each on 100 different genes.

# Analysis

## Setup

### R libraries

Calling R libraries necessary for this analysis.

```{r}
library("tidyr")
library("qtl2")
library("ggplot2")
library("dplyr")
library("biomaRt")
```

### Importing data

#### Importing eQTL data

```{r}
load("./data/DO_str_2016_eQTL.RData")
DO_pheno = DO_str_2016_cross$pheno
DO_covar = DO_str_2016_cross$covar
```

#### Importing metadata

```{r}
info_path = "./data/info/"
info_rds = list.files(path = info_path, pattern = "RDS$")
for (i in info_rds) {
  info_file_i = readRDS(paste0(info_path,i))
  if (exists("DO_eQTL_metadata")) {
    DO_eQTL_metadata = rbind(DO_eQTL_metadata,
                             info_file_i)
  } else {
    DO_eQTL_metadata = info_file_i
  }
}
rm(list = c("i","info_file_i","info_rds","info_path"))
```

#### Summarizing permutation tests

```{r}
perms_path = "./data/perms/"
perms_100_files = list.files(path = perms_path, pattern = "RDS$")
for (i in perms_100_files) {
  perm_i = readRDS(paste0(perms_path,i))
  perm_i$gene = rep(colnames(perm_i)[1], times = nrow(perm_i))
  colnames(perm_i)[1] = "lod"
  if (exists("perms_100")) {
    perms_100 = rbind(perms_100, perm_i)
  } else {
    perms_100 = perm_i
  }
}
rm(list = c("i", "perm_i","perms_path"))
perms_100$lod = as.numeric(perms_100$lod)
perms_100 = perms_100[which(!is.na(perms_100$lod)),]
perms_genes = unique(perms_100$gene)

perms_mat_100 = matrix(nrow = length(perms_genes),
                       ncol = length(perms_genes))
row.names(perms_mat_100) = perms_genes
colnames(perms_mat_100) = perms_genes
```

Plotting Wilcoxon rank-sum tests comparing distribution of each gene's permutations.

```{r}
for (i in perms_genes) {
  for (j in perms_genes) {
    perms_mat_100[i,j] = wilcox.test(perms_100[which(perms_100$gene == i),"lod"],
                                     perms_100[which(perms_100$gene == j),"lod"])$p.value
  }
}
perms_ind_100 = which(upper.tri(perms_mat_100), arr.ind = TRUE)
perms_df_100 = as.data.frame(perms_ind_100)
perms_df_100$perms = perms_mat_100[perms_ind_100]

perms_pval_hist = ggplot(data = perms_df_100, aes(x = perms)) +
  geom_histogram(fill = "#66CC66", bins = 50) +
  theme_classic() +
  xlab("P-Value") +
  ylab("Count")

perms_pval_hist
```

Getting thresholds for permutations.

```{r}
perms_1_thresh = quantile(perms_100$lod, probs = 1 - c(0, 0.05, 0.10, 0.63, 1))
p0p05 = perms_1_thresh["95%"]
p0p10 = perms_1_thresh["90%"]
p0p63 = perms_1_thresh["37%"]
```

Getting LOD peaks.

```{r}
cis_path = "./data/cis/"
LOD_files = list.files(path = cis_path, pattern = "^DO_lod_scores_cis_arrayid_\\d+.RDS$")
for (i in LOD_files) {
  LOD_scores_i = readRDS(paste0(cis_path,i))
  assign(gsub("\\.RDS","",i), LOD_scores_i)
  peaks_i = find_peaks(LOD_scores_i,
                       map = DO_str_2016_cross$pmap,
                       threshold = p0p63)
    if (exists("peaks_lod")) {
      peaks_lod = rbind(peaks_lod, peaks_i)
    } else {
      peaks_lod = peaks_i
    }
    rm(list = c("LOD_scores_i","peaks_i"))
}
rm(list = c("i"))
```

Getting genes and LOD thresholds.

```{r}
peaks_lod_2 = peaks_lod

genes_lod = unique(peaks_lod$lodcolumn)
peaks_lod$is_cis = rep(FALSE, times = nrow(peaks_lod))
peaks_lod$threshold = rep("suggestive", times = nrow(peaks_lod))
peaks_lod$threshold = ifelse(peaks_lod$lod > p0p10,
                             "ten_percent", peaks_lod$threshold)
peaks_lod$threshold = ifelse(peaks_lod$lod > p0p05,
                             "five_percent", peaks_lod$threshold)
peaks_lod$gene_chr = rep("none", times = nrow(peaks_lod))
peaks_lod$gene_pos = rep(-1000, times = nrow(peaks_lod))

for (i in genes_lod) {
  gene_i_chr = DO_eQTL_metadata[i,"chromosome_name"]
  gene_i_start = (DO_eQTL_metadata[i,"start_position"]) / 1e6
  gene_i_end = (DO_eQTL_metadata[i,"end_position"]) / 1e6
  gene_i_strand = DO_eQTL_metadata[i,"strand"]
  gene_i_position = ifelse(gene_i_strand == 1, gene_i_start, gene_i_end)
  gene_i_rows = which(peaks_lod$lodcolumn == i)
  peaks_lod[gene_i_rows,"gene_chr"] = gene_i_chr
  peaks_lod[gene_i_rows,"gene_pos"] = gene_i_position
  peaks_lod[gene_i_rows,"is_cis"] = ifelse((peaks_lod[gene_i_rows,"chr"] == gene_i_chr &
                                              peaks_lod[gene_i_rows,"pos"] > (gene_i_start - 5) &
                                              peaks_lod[gene_i_rows,"pos"] < (gene_i_end + 5)),
                                           TRUE, FALSE)
}
peaks_lod_canonical = peaks_lod[which(peaks_lod$gene_chr %in% c(1:19,"X")),]
peaks_lod_canonical$gene_chr = factor(peaks_lod_canonical$gene_chr, levels = c(1:19,"X"), ordered = TRUE)
peaks_lod_canonical$chr = factor(peaks_lod_canonical$chr, levels = c(1:19,"X"), ordered = TRUE)

lod_max = as.data.frame(peaks_lod_canonical %>% group_by(chr) %>% summarize(max_pos = max(pos)))
row.names(lod_max) = lod_max$chr
lod_max$add = rep(-1000, times = nrow(lod_max))
lod_max$med = rep(-1000, times = nrow(lod_max))
gene_max = as.data.frame(peaks_lod_canonical %>% group_by(gene_chr) %>% summarize(max_pos = max(gene_pos)))
row.names(gene_max) = gene_max$gene_chr
gene_max$add = rep(-1000, times = nrow(gene_max))
gene_max$med = rep(-1000, times = nrow(gene_max))
gap = 0
for (i in 1:nrow(lod_max)) {
  lod_length_i = lod_max[i,"max_pos"]
  gene_length_i = gene_max[i,"max_pos"]
  if (i == 1) {
    lod_max[i,"add"] = 0
    gene_max[i,"add"] = 0
    lod_max[i,"med"] = lod_length_i / 2
    gene_max[i,"med"] = gene_length_i / 2
  } else {
    lod_max[i,"add"] = lod_max[i-1,"add"] + lod_max[i-1,"max_pos"] + gap
    lod_max[i,"med"] = (lod_max[i,"add"] + lod_max[i,"add"] + lod_length_i) / 2
    gene_max[i,"add"] = gene_max[i-1,"add"] + gene_max[i-1,"max_pos"] + gap
    gene_max[i,"med"] = (gene_max[i,"add"] + gene_max[i,"add"] + gene_length_i) / 2
  }
}
```

Plotting eQTLs.

```{r}
peaks_lod_canonical$pos_add = peaks_lod_canonical$pos + lod_max[peaks_lod_canonical$chr,"add"]
peaks_lod_canonical$gene_pos_add = peaks_lod_canonical$gene_pos + gene_max[peaks_lod_canonical$gene_chr,"add"]

peaks_lod_canonical$chr17_43_49_Mb = ifelse(peaks_lod_canonical$chr == "17" &
                                           peaks_lod_canonical$pos > 43 &
                                           peaks_lod_canonical$pos < 49,
                                         "chr17_43_49_Mb", "not")
peaks_lod_canonical$color = paste(peaks_lod_canonical$is_cis,
                                  peaks_lod_canonical$chr17_43_49_Mb,
                                  sep = "_")

trans_bands = data.frame(v = c(41.557569,172.25964,103.601351,45.75523), 
                         chr = c("1","2","9","17"),
                         stringsAsFactors = FALSE)
trans_bands$pos_add = trans_bands$v + lod_max[trans_bands
                                              $chr,"add"]

eQTL_plot = ggplot(data = peaks_lod_canonical[which(peaks_lod_canonical$threshold == "five_percent"),], aes(x = pos_add, y = gene_pos_add, color = is_cis)) + 
  geom_vline(xintercept = trans_bands$pos_add, color = "#CCCCCC") +
  geom_point(size = 0.25) + 
  scale_color_manual(values = c("#666666","#999999")) + 
  xlab("Peak Position") + 
  ylab("Gene Position") +
  scale_x_continuous(breaks = lod_max$med, 
                     minor_breaks = c(lod_max$add, (lod_max["X","add"] + lod_max["X","max_pos"])), 
                     labels = lod_max$chr) +
  scale_y_continuous(breaks = gene_max$med, 
                     minor_breaks = c(gene_max$add, (gene_max["X","add"] + gene_max["X","max_pos"])), 
                     labels = gene_max$gene_chr) + 
  theme_bw()+ 
  theme(legend.position = "none", 
        panel.grid.major = element_blank()) +
  geom_rug(data = peaks_lod_canonical[which(peaks_lod_canonical$threshold == "five_percent" & !peaks_lod_canonical$is_cis),],
           aes(x = pos_add, y = gene_pos_add),
           alpha = 0.1)
eQTL_plot
```

Plotting chr17 eQTL plot.

```{r}
chr17_plot = ggplot(data = peaks_lod_canonical[which(peaks_lod_canonical$threshold == "five_percent"),], aes(x = pos_add, y = gene_pos_add, color = color, size = chr17_43_49_Mb)) + 
  geom_vline(xintercept = trans_bands$pos_add, color = "#CCCCCC", linetype = "dashed") +
  geom_point() + 
  scale_color_manual(values = c("#CC3333","#666666","#FFCC33","#999999")) + 
  xlab("Peak Position") + 
  ylab("Gene Position") +
  scale_x_continuous(breaks = lod_max$med, 
                     minor_breaks = c(lod_max$add, (lod_max["X","add"] + lod_max["X","max_pos"])), 
                     labels = lod_max$chr) +
  scale_y_continuous(breaks = gene_max$med, 
                     minor_breaks = c(gene_max$add, (gene_max["X","add"] + gene_max["X","max_pos"])), 
                     labels = gene_max$gene_chr) + 
  theme_bw()+ 
  theme(legend.position = "none", 
        panel.grid.major = element_blank()) +
  scale_size_manual(values = c(2,0.25)) +
  geom_rug(data = peaks_lod_canonical[which(peaks_lod_canonical$threshold == "five_percent" & !peaks_lod_canonical$is_cis),],
           aes(x = pos_add, y = gene_pos_add),
           color = "black", size = 0.25, alpha = 0.1)
chr17_plot
```

Plotting chr9 plot.

```{r}
peaks_lod_canonical$chr9_100_106_Mb = ifelse(as.character(peaks_lod_canonical$chr) == "9" & peaks_lod_canonical$pos >= 100 & peaks_lod_canonical$pos <= 106,
                                             "not", "IS")
peaks_lod_canonical$color_chr9 = paste(peaks_lod_canonical$is_cis, peaks_lod_canonical$chr9_100_106_Mb, sep = "_")

chr9_plot = ggplot(data = peaks_lod_canonical[which(peaks_lod_canonical$threshold == "five_percent"),], aes(x = pos_add, y = gene_pos_add, color = color_chr9, size = chr9_100_106_Mb)) + 
  geom_vline(xintercept = trans_bands[which(trans_bands$chr == "9"),"pos_add"], color = "#CCCCCC", linetype = "dashed") +
  geom_point() + 
  scale_color_manual(values = c("#666666","#CC3333","#999999","#FFCC33")) + 
  xlab("Peak Position") + 
  ylab("Gene Position") +
  scale_x_continuous(breaks = lod_max$med, 
                     minor_breaks = c(lod_max$add, (lod_max["X","add"] + lod_max["X","max_pos"])), 
                     labels = lod_max$chr) +
  scale_y_continuous(breaks = gene_max$med, 
                     minor_breaks = c(gene_max$add, (gene_max["X","add"] + gene_max["X","max_pos"])), 
                     labels = gene_max$gene_chr) + 
  theme_bw()+ 
  theme(legend.position = "none", 
        panel.grid.major = element_blank()) +
  scale_size_manual(values = c(0.25,2)) +
  geom_rug(data = peaks_lod_canonical[which(peaks_lod_canonical$threshold == "five_percent" & !peaks_lod_canonical$is_cis),],
           aes(x = pos_add, y = gene_pos_add),
           color = "black", size = 0.25, alpha = 0.1)
chr9_plot
```

Getting annotation for genes

```{r}
genes = unique(peaks_lod_canonical$lodcolumn)
maRt = useMart(biomart = "ENSEMBL_MART_ENSEMBL",
               host = "https://jan2019.archive.ensembl.org",
               dataset = "mmusculus_gene_ensembl")
maRt_filter = "ensembl_gene_id"
maRt_attributes = c("mgi_symbol","mgi_description","mgi_id","chromosome_name","start_position",
                    "end_position","strand","ensembl_gene_id")
Mm_maRt = getBM(maRt_attributes, maRt_filter, genes, maRt)
row.names(Mm_maRt) = Mm_maRt$ensembl_gene_id
annotated_peaks = cbind(Mm_maRt[peaks_lod_canonical$lodcolumn,],
                        peaks_lod_canonical) 
row.names(annotated_peaks) = 1:nrow(annotated_peaks)
```

Saving annotated peaks and plots.

```{r}
save(list = ls(pattern = "plot$"), file = "./data/eQTL_plots.RData")
saveRDS(annotated_peaks, "./data/eQTL_annotated_peaks.RDS")
```

### Output

The output data are saved in `./data/`.

### Document Control

This document was prepared using RMarkdown in RStudio.
