---
title: "DO RTG Expression Interpretation"
author: "Michael C. Saul (michael.saul [at] jax.org)"
output: workflowr::wflow_html
---

# Background

## Motivation

### Purpose of analysis

This script is used to correlate RTG calculated traits to expression.

### R libraries

Calling R libraries necessary for this analysis.

```{r}
library("limma")
library("edgeR")
library("ggplot2")
library("biomaRt")
library("statmod")
library("qvalue")
```

### Getting publication themes

```{r}
source("./code/ggplot_pub_themes.R")
```

### `norm_rank_transform()` function

Getting a normal rank transformation function that can handle `NA` values.

```{r}
norm_rank_transform = function(x, c = (0)) {
  stopifnot(is.numeric(x) & is.vector(x))
  x_noNA = which(!is.na(x))
  N = length(x_noNA)
  x[x_noNA] = qnorm((rank(x[x_noNA], ties.method = "average") - c) / (N - (2 * c) + 1))
  return(x)
}
```

### Importing data

Importing data.

```{r}
DO_pheno       = readRDS("./data/DO_416_pheno.RDS")
DO_dge         = readRDS("./data/DO_416_DGEList.RDS")
DO_RTG_analysis_1 = readRDS("./data/DO_IVSA_prediction_a1_ACQUISITION_logit.RDS")
DO_RTG_analysis_2 = readRDS("./data/DO_IVSA_prediction_a2_AQ_cancor.RDS")
DO_RTG_analysis_3 = readRDS("./data/DO_IVSA_prediction_a3_ALL_cancor.RDS")
DO_pheno$RTG_a1 = DO_RTG_analysis_1[row.names(DO_pheno)]
DO_pheno$RTG_a2 = DO_RTG_analysis_2[row.names(DO_pheno),"IVSA_novelty_cancor"]
DO_pheno$RTG_a3 = DO_RTG_analysis_3[row.names(DO_pheno),"IVSA_novelty_cancor"]
has_RTG_a1_express = row.names(DO_pheno[which((!is.na(DO_pheno[,"RTG_a1"])) & (DO_pheno$Sex == "M" | DO_pheno$Sex == "F")),])
has_RTG_a2_express = row.names(DO_pheno[which((!is.na(DO_pheno[,"RTG_a2"])) & (DO_pheno$Sex == "M" | DO_pheno$Sex == "F")),])
has_RTG_a3_express = row.names(DO_pheno[which((!is.na(DO_pheno[,"RTG_a3"])) & (DO_pheno$Sex == "M" | DO_pheno$Sex == "F")),])
```

Getting top tables for RTG analyses 1-3.

```{r}
DO_RTG_a1_toptable = readRDS("./data/DO_rtg_a1_toptable_annotated.RDS")
DO_RTG_a2_toptable = readRDS("./data/DO_rtg_a2_toptable_annotated.RDS")
DO_RTG_a3_toptable = readRDS("./data/DO_rtg_a3_toptable_annotated.RDS")
```

## Gene Expression Interpretation

### Top tables

Looking at top genes in analyses 1-3.

```{r}
DO_RTG_a1_toptable[which(DO_RTG_a1_toptable$qvalue < 0.1),]
```

```{r}
DO_RTG_a2_toptable[which(DO_RTG_a2_toptable$qvalue < 0.1),]
```

```{r}
DO_RTG_a3_toptable[which(DO_RTG_a3_toptable$qvalue < 0.1),]
```

Particularly interesting genes from this perspective include *Gpr17*, which is significant in both analysis 1 and analysis 2. Because the interpretation of analysis 1 is the most straightforward, plotting the correlation of *Gpr17* expression and analysis 1.

```{r}
Gpr17_ensembl_id = "ENSMUSG00000052229"
DO_pheno$Gpr17 = cpm(DO_dge)[Gpr17_ensembl_id,row.names(DO_pheno)]
Gpr17_lm = lm(RTG_a3 ~ Gpr17, data = DO_pheno[has_RTG_a3_express,])
Gpr17_cor = cor(DO_pheno[has_RTG_a1_express,"Gpr17"],
                DO_pheno[has_RTG_a1_express,"RTG_a3"])
Gpr17_xlab_title = expression(paste(italic("Gpr17"), " Striatum Expression", sep = ""))
Gpr17_bivariate_plot = ggplot(data = DO_pheno[has_RTG_a3_express,], aes(x = Gpr17, y = RTG_a3, color = Sex)) +
  geom_point(size = pt_to_mm * 2) +
  scale_color_manual(values = c("#3399CC","#66CC66")) +
  geom_abline(aes(intercept = Gpr17_lm$coefficients[1], 
                  slope = Gpr17_lm$coefficients[2]),
              color = "#000000", size = (pt_to_mm * 1)) +
  ylab("Reference Trait Analysis: Analysis 3 (All IVSA Traits)") +
  xlab(Gpr17_xlab_title) +
  theme_classic()
Gpr17_bivariate_plot
```

Saving the *Gpr17* bivariate plot.

```{r}
ggsave(file = "./data/figures/Gpr17_bivariate_a1_plot.pdf",
       plot = Gpr17_bivariate_plot + pubtheme_classic,
       width = 3, height = 3, units = "in")
```

### Looking at three-way intersection

```{r}
a1_q_0p10 = DO_RTG_a1_toptable[which(DO_RTG_a1_toptable$qvalue < 0.10),"ensembl_gene_id"]
a2_q_0p10 = DO_RTG_a2_toptable[which(DO_RTG_a2_toptable$qvalue < 0.10),"ensembl_gene_id"]
a3_q_0p10 = DO_RTG_a3_toptable[which(DO_RTG_a3_toptable$qvalue < 0.10),"ensembl_gene_id"]
threeway_intersect_q_0p10 = intersect(intersect(a1_q_0p10,a2_q_0p10),a3_q_0p10)
DO_RTG_a3_toptable[threeway_intersect_q_0p10,]
```

### Output

The output data are saved in `./data/`.

### Document Control

This document was prepared using RMarkdown in RStudio.
