---
title: "DO RTG Projection for Mapping"
author: "Michael C. Saul (michael.saul [at] jax.org)"
output: workflowr::wflow_html
---

# Background

## Motivation

### Purpose of analysis

This script is used to calculate RTG projections for mapping work.

### R libraries

Calling R libraries necessary for this analysis.

```{r}
library("ggplot2")
```

### Getting publication themes

```{r}
source("./code/ggplot_pub_themes.R")
```

### Importing data

Importing data.

```{r}
# Loading RTG analyses
DO_RTG_analysis_1 = readRDS("./data/DO_IVSA_prediction_a1_ACQUISITION_logit.RDS")
DO_RTG_analysis_2 = readRDS("./data/DO_IVSA_prediction_a2_AQ_cancor.RDS")
DO_RTG_analysis_3 = readRDS("./data/DO_IVSA_prediction_a3_ALL_cancor.RDS")

# Loading novelty response data frame
DO_novelty_response_raw = readRDS("./data/DO_novelty_response_data.RDS")
```

### Making Reference Traits Analysis Data Frame

Saving RTG analysis projections as data frame.

```{r}
# Writing out projection
DO_RTG_project_df = DO_novelty_response_raw[,c("Mouse_ID","Sex","Study","Generation","Group")]

DO_RTG_project_df$RTG_a1 = DO_RTG_analysis_1[row.names(DO_RTG_project_df)]
DO_RTG_project_df$RTG_a2 = DO_RTG_analysis_2[row.names(DO_RTG_project_df),"IVSA_novelty_cancor"]
DO_RTG_project_df$RTG_a3 = DO_RTG_analysis_3[row.names(DO_RTG_project_df),"IVSA_novelty_cancor"]
```

Saving projection data frame.

```{r}
saveRDS(DO_RTG_project_df,"./data/DO_RTG_project_df_for_mapping.RDS")
```

### Output

The output data are saved in `./data/`.

### Document Control

This document was prepared using RMarkdown in RStudio.