---
title: "DO RTG Coexpression Analysis"
author: "Michael C. Saul (michael.saul [at] jax.org)"
output: workflowr::wflow_html
---

# Background

## Motivation

### Purpose of analysis

This script is used to perform WGCNA for the reference trait analysis.

# Analysis

## Setup

### R libraries

Calling R libraries necessary for this analysis.

```{r}
library("limma")
library("edgeR")
library("ggplot2")
library("ggbeeswarm")
library("gplots")
library("RColorBrewer")
library("data.table")
library("biomaRt")
library("statmod")
library("WGCNA")
library("MASS")
library("msaul")
library("cliqueR")
```

### Getting `norm_rank_transform` function

```{r}
norm_rank_transform = function(x, c = (0)) {
  stopifnot(is.numeric(x) & is.vector(x))
  N = length(x)
  return(qnorm((rank(x) - c) / (N - (2 * c) + 1)))
}
```

### Importing data

```{r}
# Bringing in expression objects
DO_voom = readRDS("./data/DO_416_voom.RDS")
DO_pheno = readRDS("./data/DO_416_pheno.RDS")

# Bringing in RTG objects
DO_RTG_a1 = readRDS("./data/DO_IVSA_prediction_ACQUISITION_logit.RDS")
DO_RTG_a2 = readRDS("./data/DO_IVSA_prediction_AQ_cancor.RDS")
DO_RTG_a3 = readRDS("./data/DO_IVSA_prediction_ALL_cancor.RDS")

# Bringing in RTG top tables
DO_RTG_a1_toptable = readRDS("./data/DO_rtg_a1_toptable_annotated.RDS")
DO_RTG_a2_toptable = readRDS("./data/DO_rtg_a2_toptable_annotated.RDS")
DO_RTG_a3_toptable = readRDS("./data/DO_rtg_a3_toptable_annotated.RDS")
```

Setting number of permutations for MSET enrichment analysis.

```{r}
MSET_B = 1e6
```

### Adjusting data to get residuals after choroid plexus regression

```{r}
DO_log2_choroid_plexus = log2(DO_pheno$choroid_plexus_covariate)
names(DO_log2_choroid_plexus) = row.names(DO_pheno)
DO_log2_choroid_plexus = DO_log2_choroid_plexus[colnames(DO_voom)]
DO_voom_cpnorm = matrix(nrow = nrow(DO_voom$E), ncol = ncol(DO_voom$E))
row.names(DO_voom_cpnorm) = row.names(DO_voom)
colnames(DO_voom_cpnorm) = colnames(DO_voom)
for (i in 1:nrow(DO_voom_cpnorm)) {
  gene_i = row.names(DO_voom_cpnorm)[i]
  DO_voom_cpnorm[gene_i,] = norm_rank_transform(resid(lm(DO_voom$E[gene_i,] ~ DO_log2_choroid_plexus)))
}
saveRDS(DO_voom_cpnorm,"./data/DO_416_voom_cpresiduals.RDS",compress="xz")
```

## Running WGCNA

### Querying good samples

Making sure there are no genes that have too many missing values or are zero variance.

```{r}
DO_wgcna_gsg = goodSamplesGenes(t(DO_voom_cpnorm))
ifelse(DO_wgcna_gsg$allOK,
       "All genes are good and all samples are good.",
       "There are bad samples or genes.")
```

### Finding soft threshold

```{r}
powers = c(c(1:10), seq(from = 12, to=20, by=2))
DO_wgcna_sft = pickSoftThreshold(t(DO_voom_cpnorm),
                                 powerVector = powers,
                                 networkType="signed",
                                 corFnc = bicor)
```

Plotting scale-free topology fit

```{r}
plot(x = DO_wgcna_sft$fitIndices$Power, 
     DO_wgcna_sft$fitIndices$SFT.R.sq, 
     xlab = "Soft Threshold (power)", 
     ylab = "R-Squared", type ="l", 
     col = "dark gray", main = "Scale Independence (all)")
text(DO_wgcna_sft$fitIndices$Power, 
     DO_wgcna_sft$fitIndices$SFT.R.sq, 
     labels = powers, col ="#3399CC")
abline(h = 0.9, col = "#FF3333")
```

Plotting median connectivity

```{r}
plot(x = DO_wgcna_sft$fitIndices$Power, 
     y = DO_wgcna_sft$fitIndices$median.k, 
     xlab = "Soft Threshold (powers)",
     ylab = "Median Connectivity", 
     main = "Median Connectivity (all)", 
     col = "dark gray", type = "l")
text(DO_wgcna_sft$fitIndices$Power, DO_wgcna_sft$fitIndices$median.k., labels = powers, col = "#3399CC")
```

A soft threshold of 3 appears to be appropriate for these data. Running signed WGCNA with this soft threshold for each dataset.

```{r}
DO_modules = blockwiseModules(t(DO_voom_cpnorm), power = 3,
                              networkType = "signed",
                              minModuleSize = 30,
                              corType= "bicor",
                              maxBlockSize = 30000,
                              numericLabels = TRUE,
                              saveTOMs = FALSE,
                              verbose = 3)
```

Getting module eigengene information and assigning colors

```{r}
DO_colors = labels2colors(DO_modules$colors)
DO_eigengenes = DO_modules$MEs
```

Finding relationship between eigengenes and phenotype data of interest

```{r}
# Putting RTG data into DO_pheno
DO_pheno$RTG_a1 = DO_RTG_a1[row.names(DO_pheno)]
DO_pheno$RTG_a2 = DO_RTG_a2[row.names(DO_pheno),"IVSA_novelty_cancor"]
DO_pheno$RTG_a3 = DO_RTG_a3[row.names(DO_pheno),"IVSA_novelty_cancor"]

# Finding significance for each factor in the eigengenes
DO_phenotypes_cor = c("RTG_a1","RTG_a2","RTG_a3")

DO_eigengene_significance = data.frame(matrix(nrow = ncol(DO_eigengenes), ncol = 1 + (3 * length(DO_phenotypes_cor))))
row.names(DO_eigengene_significance) = colnames(DO_eigengenes)
colnames(DO_eigengene_significance) = c("Eigengene",
                                        paste(DO_phenotypes_cor,"_bicor_p",sep=""),
                                        paste(DO_phenotypes_cor,"_membership_p",sep=""),
                                        paste(DO_phenotypes_cor,"_overlap_p",sep=""))
DO_eigengene_significance$Eigengene = colnames(DO_eigengenes)

for (i in 1:ncol(DO_eigengenes)) {
  eigengene_i = DO_eigengene_significance[i,"Eigengene"]
  for (j in DO_phenotypes_cor) {
    col_j = paste(j,"_bicor_p",sep="")
    DO_eigengene_significance[i,col_j] = bicorAndPvalue(DO_eigengenes[,eigengene_i],
                                                        DO_pheno[,j],
                                                        use = "pairwise.complete.obs")$p[1,1]
  }
}

for (i in DO_phenotypes_cor) {
  col_i = paste(i,"_overlap_p",sep="")
  toptable_i = eval(parse(text = paste("DO_",i,"_toptable",sep="")))
  sig_genes_i = toptable_i[which(toptable_i$qvalue < 0.10),"ensembl_gene_id"]
  for (j in 1:ncol(DO_eigengenes)) {
    eigengene_j = DO_eigengene_significance[j,"Eigengene"]
    module_genes_j = row.names(DO_voom_cpnorm)[which(DO_modules$colors == as.numeric(gsub("^ME","",eigengene_j)))]
    DO_eigengene_significance[j,col_i] = MSET.overlap.test(sig_genes_i,
                                                           module_genes_j,
                                                           toptable_i$ensembl_gene_id,
                                                           row.names(DO_voom_cpnorm), 
                                                           B = MSET_B)$p.value + (1/MSET_B)
  }
}
```

### Module Membership Values

Getting module membership values for all genes. Flagging outlier observations by changing observations to NA if they have a genewise Bonferroni-corrected externally-studentized residual p-value of 0.001 or less relative to the module eigengene and if there are no more than 2 such flagged outliers.

```{r}
DO_module_membership = as.data.frame(matrix(ncol = 4 + length(DO_phenotypes_cor), nrow = nrow(DO_voom_cpnorm)))
row.names(DO_module_membership) = row.names(DO_voom_cpnorm) 
colnames(DO_module_membership) = c("ID",
                                   "module",
                                   "color",
                                   "module_membership",
                                   DO_phenotypes_cor) 
DO_module_membership$ID = row.names(DO_voom_cpnorm)
DO_module_membership$module = DO_modules$colors 
DO_module_membership$color = DO_colors
DO_voom_cpnorm_original = DO_voom_cpnorm

for (i in 1:nrow(DO_module_membership)) {
  current_id = DO_module_membership[i,"ID"]
  current_module = DO_module_membership[i,"module"]
  current_eigengene = paste("ME",current_module,sep="") 
  current_studres = studres(lm(DO_voom_cpnorm[i,] ~ DO_eigengenes[,current_eigengene]))
  current_bon_studres = ncol(DO_voom_cpnorm) * 2 * ifelse(current_studres < 0,
                                                          pnorm(current_studres, lower.tail = TRUE),
                                                          pnorm(current_studres, lower.tail = FALSE))
  current_bon_studres = ifelse(current_bon_studres >= 1, 1, current_bon_studres)
  if (length(which(current_bon_studres < 0.001)) > 0 & length(which(current_bon_studres < 0.001)) <= 2) {
    DO_voom_cpnorm[i,which(current_bon_studres < 0.001)] = NA
  }
  DO_module_membership[i,"module_membership"] = bicor(DO_eigengenes[,current_eigengene],DO_voom_cpnorm[i,],
                                                      use = "pairwise.complete.obs")
  for (j in DO_phenotypes_cor) {
    DO_module_membership[current_id,j] = bicor(DO_voom_cpnorm[current_id,],
                                               norm_rank_transform(DO_pheno[,j]),
                                               use = "pairwise.complete.obs")
  }
}

saveRDS(DO_voom_cpnorm,"./data/DO_voom_cpresiduals_NArm.RDS",compress="xz")

DO_eigengene_membership_cor = as.data.frame(matrix(nrow = nrow(DO_eigengene_significance),
                                                   ncol = length(DO_phenotypes_cor)),
                                            stringsAsFactors = FALSE)
row.names(DO_eigengene_membership_cor) = DO_eigengene_significance$Eigengene
colnames(DO_eigengene_membership_cor) = DO_phenotypes_cor

for (i in 1:nrow(DO_eigengene_significance)) {
  module_i = as.numeric(gsub("^ME","",DO_eigengene_significance[i,"Eigengene"]))
  rows_i = which(DO_module_membership$module == module_i)
  for (j in DO_phenotypes_cor) {
    col_j = paste(j, "_membership_p", sep = "")
    DO_eigengene_membership_cor[paste("ME",module_i,sep=""),j] = bicor(DO_module_membership[rows_i,j],
                                                                       DO_module_membership[rows_i,"module_membership"],
                                                                       use = "pairwise.complete.obs")
    DO_eigengene_significance[i,col_j] = bicorAndPvalue(DO_module_membership[rows_i,j],
                                                        DO_module_membership[rows_i,"module_membership"],
                                                        use = "pairwise.complete.obs")$p[1,1]
  }
}
```

Writing out WGCNA module membership data

```{r}
saveRDS(DO_module_membership,
        "./data/DO_module_membership.RDS",
        compress="xz")
saveRDS(DO_modules,
        "./data/DO_wgcna.RDS",
        compress="xz")
saveRDS(DO_eigengene_significance,
        "./data/DO_eigengene_significance.RDS",
        compress="xz")
saveRDS(DO_eigengenes,
        "./data/DO_eigengenes.RDS",
        compress="xz")
```

### Getting correlation tables

```{r}
DO_cortable = bicor(t(DO_voom_cpnorm_original),
                    use = "pairwise.complete.obs")
DO_highcor = as.data.table(which(abs(DO_cortable) >= 0.5, arr.ind = TRUE))
DO_highcor = DO_highcor[row < col]
DO_highcor = data.frame(gene_1 = row.names(DO_cortable)[DO_highcor$row],
                        gene_2 = colnames(DO_cortable)[DO_highcor$col],
                        cor = DO_cortable[as.matrix(DO_highcor)],
                        stringsAsFactors = FALSE)
rm(list = c("DO_cortable"))

saveRDS(DO_highcor,"./data/DO_highcor_cpresiduals_datatable.RDS",compress="xz")
```

### Running paraclique analysis

First, making file with paraclique information on thresholded data

```{r}
# Getting number of nodes (vertices) and edges
n_nodes = length(unique(c(DO_highcor$gene_1, DO_highcor$gene_2)))
n_edges = nrow(DO_highcor)

# Making file to write out
DO_write_out_pc_cor_table = DO_highcor[,1:2]
colnames(DO_write_out_pc_cor_table) = c(n_nodes, n_edges)
write.table(DO_write_out_pc_cor_table, "./data/DO_paraclique_data.el", sep = " ", quote = FALSE, row.names = FALSE, col.names = TRUE)

# Getting paracliques (minimum clique size = 5, minimum paraclique size = 10, glom factor = 0.2)
# Note: this is not the traditional glom factor. 
# Instead, it is the proportion of edges that each added node must have to the total number of nodes.
clique_min = 5
paraclique_min = 10
glom_factor = 0.2 
DO_paracliques = cliqueR.paraclique(filename = "./data/DO_paraclique_data.el", 
                                    igf = glom_factor, min_mc_size = clique_min, min_pc_size = paraclique_min)

# Getting eigenvalues for paracliques
for (i in 1:length(DO_paracliques)) {
  genes_i = DO_paracliques[[i]]
  eigengene_i = prcomp(t(DO_voom_cpnorm_original[genes_i,]), scale = TRUE, center = TRUE)$x[,1]
  if (exists("DO_paraclique_eigengenes")) {
    DO_paraclique_eigengenes[,paste("PCE",i,sep="")] = eigengene_i[DO_paraclique_eigengenes$SubjectID]
  } else {
    DO_paraclique_eigengenes = data.frame(row.names = names(eigengene_i),
                                          SubjectID = as.character(names(eigengene_i)),
                                          PCE1 = eigengene_i,
                                          stringsAsFactors = FALSE)
  }
}
```

Next, evaluating paracliques for significance with respect to RTG analyses.

```{r}
DO_paraclique_significance = data.frame(matrix(nrow = (ncol(DO_paraclique_eigengenes) - 1), ncol = 1 + (2 * length(DO_phenotypes_cor))))
row.names(DO_paraclique_significance) = colnames(DO_paraclique_eigengenes)[-1]
colnames(DO_paraclique_significance) = c("paraclique",
                                         paste(DO_phenotypes_cor,"_bicor_p",sep=""),
                                         paste(DO_phenotypes_cor,"_overlap_p",sep=""))
DO_paraclique_significance$paraclique = colnames(DO_paraclique_eigengenes)[-1]

for (i in 1:nrow(DO_paraclique_significance)) {
  paraclique_i = DO_paraclique_significance[i,"paraclique"]
  for (j in DO_phenotypes_cor) {
    col_j = paste(j,"_bicor_p",sep="")
    DO_paraclique_significance[i,col_j] = bicorAndPvalue(DO_paraclique_eigengenes[,paraclique_i],
                                                         DO_pheno[,j],
                                                         use = "pairwise.complete.obs")$p[1,1]
  }
}

for (i in DO_phenotypes_cor) {
  col_i = paste(i,"_overlap_p",sep="")
  toptable_i = eval(parse(text = paste("DO_",i,"_toptable",sep="")))
  sig_genes_i = toptable_i[which(toptable_i$qvalue < 0.10),"ensembl_gene_id"]
  for (j in 1:length(DO_paracliques)) {
    paraclique_genes_j =  DO_paracliques[[j]]
    DO_paraclique_significance[j,col_i] = MSET.overlap.test(sig_genes_i,
                                                            paraclique_genes_j,
                                                            toptable_i$ensembl_gene_id,
                                                            row.names(DO_voom_cpnorm), 
                                                            B = MSET_B)$p.value + (1/MSET_B)
  }
}
```

Next, writing out paraclique data.

```{r}
saveRDS(DO_paraclique_eigengenes, "./data/DO_paraclique_eigengenes.RDS")
saveRDS(DO_paracliques, "./data/DO_paracliques.RDS")
saveRDS(DO_paraclique_significance, "./data/DO_paracliques_significance.RDS")
```

### Document Control

This document was prepared using RMarkdown in RStudio.
