---
title: "DO RTG Coexpression Mapping"
author: "Michael C. Saul (michael.saul [at] jax.org)"
output: workflowr::wflow_html
---

# Background

## Motivation

### Purpose of analysis

This script is used to map WGCNA and paraclique eigengenes.

# Analysis

## Setup

### R libraries

Calling R libraries necessary for this analysis.

```{r}
library("limma")
library("edgeR")
library("ggplot2")
library("ggbeeswarm")
library("gplots")
library("RColorBrewer")
library("data.table")
library("biomaRt")
library("statmod")
library("WGCNA")
library("MASS")
library("qtl2")
```

### Getting `norm_rank_transform` function

```{r}
norm_rank_transform = function(x, c = (0)) {
  stopifnot(is.numeric(x) & is.vector(x))
  N = length(x)
  return(qnorm((rank(x) - c) / (N - (2 * c) + 1)))
}
```

### Importing data

```{r}
# Bringing in eigengene objects and giving it row names
DO_WGCNA_eigengenes = readRDS("./data/DO_eigengenes.RDS")
DO_PCE_eigengenes = readRDS("./data/DO_paraclique_eigengenes.RDS")
DO_exprs = readRDS("./data/DO_416_voom_cpresiduals.RDS")
row.names(DO_WGCNA_eigengenes) = colnames(DO_exprs)
rm(list = c("DO_exprs"))

# Bringing in expression QTL data
load("./data/DO_str_2016_eQTL.RData")

# Getting covariates
DO_covar = DO_str_2016_cross$covar
addcovar_mat = model.matrix(~ ngen + sex, data = DO_covar)[,-1]
```

Matching eigengene data with cross data

```{r}
DO_eigengenes_cross = DO_WGCNA_eigengenes[gsub("^(\\d{4,5})_.*$","\\1",row.names(DO_str_2016_cross$pheno)),]
DO_eigengenes_cross = cbind(DO_eigengenes_cross, DO_PCE_eigengenes[row.names(DO_eigengenes_cross),-1])
row.names(DO_eigengenes_cross) = row.names(DO_str_2016_cross$pheno)
DO_eigengenes_cross = as.matrix(DO_eigengenes_cross)
```

### Running `scan1()` for all modules

```{r}
# Looping through all coexpression module/paraclique eigengenes to make crosses
for (i in colnames(DO_eigengenes_cross)) {
  ME_cross_i = scan1(genoprobs = DO_str_2016_aprobs,
                     pheno = DO_eigengenes_cross[,i],
                     kinship = DO_str_2016_kinship,
                     addcovar = addcovar_mat,
                     cores = 2)
  colnames(ME_cross_i) = i
  if (exists("ME_crosses")) {
    ME_crosses = cbind(ME_crosses, ME_cross_i)
  } else {
    ME_crosses = ME_cross_i
  }
}
```

### Getting peaks for all modules

```{r}
# Finding peaks with LOD scores >= 6
ME_peaks = find_peaks(ME_crosses, map = DO_str_2016_cross$pmap, threshold = 6, prob = 0.95)
ME_peaks[order(ME_peaks$lod),]
```

### Saving output

```{r}
saveRDS(ME_peaks, "./data/DO_mQTL_peaks.RDS", compress = "xz")
saveRDS(ME_crosses, "./data/DO_mQTL_scan1s.RDS", compress = "xz")
```

### Document Control

This document was prepared using RMarkdown in RStudio.