---
title: "20_predict_acquisition_from_novelty"
author: "Robyn L Ball,  PhD"
date: "9/17/2020"
output: workflowr::wflow_html
---


# PURPOSE 

Using DO_novelty.RDS data derived in 11, predict aquisition

# METHODS

1. import DO_novelty_response_data.RDS as novelty response data from "11_DO_novelty_response_summarize"
2. import DO_IVSA_raw_data and preprocess similar to "12_DO_IVSA_novelty_cancor"
3. assess which novelty response variables predict aquisition using elastic net using a multivariate response:

Y is a matrix of
+ Rate of acquistion: 1 - proportion of sessions to acquisition (or end of the pipeline)
+ Amount of cocaine: total infused divided by the number of sessions to acquistion (or end of the pipeline)
+ Amount of active lever presses, accounting for activity: ratio of total active lever presses to total inactive lever presses over all sessions
+ Consistency: coefficient of variation of active lever presses across all sessions

4. Predict Y for all animals with novelty response data
5. Export for analysis

For details on IVSA protocol, see file:///Users/rlb/Documents/saul/doc/60cocaineivsa2019.pdf

# CODE

set options, load packages

```{r}
options(stringsAsFactors = FALSE)
library(ggplot2)
library(glmnet)
library(knitr)
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```

read in novelty data and raw IVSA data

```{r}
DO_novelty = readRDS("./data/DO_novelty_response_data.RDS")
nov_raw <- read.csv("./data/raw/Novelty_raw_datarelease_JDO_Q12020.0.1.csv", comment.char = "%",
                                     na.strings = c("NA","#N/A",""))

# for raw data, group = dataset
nov_raw$dataset <- rep("precenter", nrow(nov_raw))
nov_raw$dataset[which(nov_raw$Group=="post_center")] <- "CSNA"
nov_raw$DE_Sex <- "F"
nov_raw$DE_Sex[which(nov_raw$Sex=="Male")] <- "M"

colnames(nov_raw) <- gsub("\\.", "_", colnames(nov_raw))
DO_IVSA = readRDS("./data/DO_IVSA_raw_data.RDS")
IVSA_metadata = readRDS("./data/IVSA_metadata_sheet.RDS")
```

## Explore 

```{r}
dim(DO_novelty)
#colnames(DO_novelty)
dim(DO_IVSA)
dim(nov_raw)
```

find Troyler

```{r}
tcols <- grep("tester", colnames(DO_novelty))
table(DO_novelty[, tcols[1]])
```

tag any that are "TAR" or "TRTW" as Trowler

```{r}
DO_novelty$Troyler <- as.numeric(DO_novelty[, tcols[1]] %in% c("TAR", "TRTW") | DO_novelty[, tcols[2]] %in% c("TAR", "TRTW") |
                                   DO_novelty[, tcols[3]] %in% c("TAR", "TRTW")
                                   )
table(DO_novelty$Troyler)
```

```{r}
table(DO_novelty[, c("Group", "Troyler")])
```

```{r}
apply(IVSA_metadata[IVSA_metadata$vartype=="Acquisition", ], 2, function(x) {length(unique(x))})
```
 2 doses, 51 sessions, 9 blocks
 
```{r}
unique(IVSA_metadata[IVSA_metadata$vartype=="Acquisition", 4:7])
```
 what are the NA blocks? 
 
```{r}
table(IVSA_metadata[IVSA_metadata$vartype=="Acquisition", c("block", "session")], useNA = "ifany")
```
 
It seems the NA block is really the 9th block. let's see 

```{r}
is_set <- which(IVSA_metadata$vartype=="Acquisition" & is.na(IVSA_metadata$block) &!is.na(IVSA_metadata$session))
unique(IVSA_metadata$is_total[is_set])
```
not all are totals

```{r}
is_set <- which(IVSA_metadata$vartype=="Acquisition" & is.na(IVSA_metadata$block) & !IVSA_metadata$is_total)
unique(IVSA_metadata$long_varname[is_set])
```

if block == NA, it is either a total or it is the SessionsToAquisition

Is it the same for sessions?

```{r}
is_set <- which(IVSA_metadata$vartype=="Acquisition" & is.na(IVSA_metadata$session))
unique(IVSA_metadata$long_varname[is_set])
```

so if block == NA && session == NA, it is the SessionsToAcquisition

```{r}
is_set <- which(IVSA_metadata$vartype=="DoseResponse" & is.na(IVSA_metadata$block) & is.na(IVSA_metadata$session) & IVSA_metadata$is_total & IVSA_metadata$dose_mgperkg==1)
is_set2 <- is_set[grep("Inf", IVSA_metadata$variable[is_set])]
IVSA_metadata[is_set2, c("variable", "long_varname")]
```

Could use the percentage of active lever presses per session: AQ_pAP_Total_s{01}
```{r}
is_set <- which(IVSA_metadata$vartype=="DoseResponse" & is.na(IVSA_metadata$block) & is.na(IVSA_metadata$session) & IVSA_metadata$is_total & IVSA_metadata$dose_mgperkg==1)
is_set2 <- is_set[grep("ILP", IVSA_metadata$variable[is_set])]
IVSA_metadata[is_set2, c("variable", "long_varname")]
```

```{r}
is_set <- which(IVSA_metadata$vartype=="DoseResponse" & is.na(IVSA_metadata$block) & is.na(IVSA_metadata$session)  & IVSA_metadata$dose_mgperkg==1)
is_set2 <- is_set[grep("CoV", IVSA_metadata$variable[is_set])]
IVSA_metadata[is_set2, c("variable", "long_varname")]
```

### Multivariate response, Y

For active lever presses, accounting for activity, use : DR_ALP_TfASoTD_1p0mgkg (Dose Response FR1-Active_LeverPresses_TotalForAllSessionsOnThisDose-1.0 mg/kg) divided by 
DR_ILP_TfASoTD_1p0mgkg (Dose Response FR1-InactiveLeverPresses_TotalForAllSessionsOnThisDose-1.0 mg/kg)

For mean amount of cocaine per session use: DR_Inf_TfASoTD_1p0mgkg: Dose Response FR1-Infusions_TotalForAllSessionsOnThisDose-1.0 mg/kg divided by the number of sessions

For consistency, use: DR_IEI_CoV_ALP_Total_1p0mgkg: Dose response FR1-InterEventInterval_CoefOfVariation_ActiveLeverPresses_Total-1.0 mg/kg

For rate of acquistion, use 1 - SessionsToAcquisition/28

### Getting IVSA metadata.

```{r}
IVSA_DE_vars = IVSA_metadata[which(IVSA_metadata$vartype == "Descriptive"),"variable"]

# Removing data columns broken down by sessions and blocks
IVSA_AQ_vars_noblocks_nosessions = IVSA_metadata[which(is.na(IVSA_metadata$session) &
                                                         is.na(IVSA_metadata$block) &
                                                         IVSA_metadata$vartype == "Acquisition"),
                                                 "variable"]

# Removing data columns not at 0.032, 0.1, 0.32, and 1 mg/kg
# this make a compatible dataset between precenter and center data
IVSA_DR_currentdoses = c(0.032, 0.1, 0.32, 1.0)

IVSA_DR_vars_currentprotocol = IVSA_metadata[which(is.na(IVSA_metadata$session) &
                                                     is.na(IVSA_metadata$block) &
                                                     IVSA_metadata$vartype == "DoseResponse" &
                                                     IVSA_metadata$dose_mgperkg %in% IVSA_DR_currentdoses),
                                             "variable"]

IVSA_EX_noblocks = IVSA_metadata[which(is.na(IVSA_metadata$block) &
                                         IVSA_metadata$vartype == "Extinction"),
                                 "variable"]

IVSA_RI_noblocks = IVSA_metadata[which(is.na(IVSA_metadata$block) &
                                         IVSA_metadata$vartype == "Reinstatement"),
                                 "variable"]

IVSA_data_vars = c(IVSA_AQ_vars_noblocks_nosessions,
                   IVSA_DR_vars_currentprotocol,
                   IVSA_EX_noblocks,
                   IVSA_RI_noblocks)
```

Appending the value of `28` to IVSA animals that did not acquire.

This is the maximum number of sessions and indicates they finshed the pipeline

## TODO: Fix this in case there were differences. Check Troy's email.

```{r}
summary(DO_IVSA$AQ_SessionsToAcquisition)
DO_IVSA$AQ_SessionsToAcquisition = ifelse(DO_IVSA$DE_Exit_Reason == "IVSA Acquisition Only",
                                          28, DO_IVSA$AQ_SessionsToAcquisition)
summary(DO_IVSA$AQ_SessionsToAcquisition)
```

#### Novelty response: consider precenter confounding

We know there is confounding with precenter vs CSNA data. Use rank Z normalization separately for precenter and CSNA data and include a indicator variable for 'precenter' in the analysis.


```{r}
# Getting behavior novelty columns
DO_novelty_cols = colnames(DO_novelty)

# Open field
DO_novelty_OFA_cols = DO_novelty_cols[grep("^OFA_.*$",DO_novelty_cols)]
DO_novelty_OFA_cols = DO_novelty_OFA_cols[-1 * which(DO_novelty_OFA_cols %in% c("OFA_date_of_test","OFA_tester"))]

# Light/Dark
DO_novelty_LD_cols = DO_novelty_cols[grep("^LD_.*$",DO_novelty_cols)]
DO_novelty_LD_cols = DO_novelty_LD_cols[-1 * which(DO_novelty_LD_cols %in% c("LD_date_of_test","LD_tester"))]

# Hole board
DO_novelty_HB_cols = DO_novelty_cols[grep("^HB_.*$",DO_novelty_cols)]
DO_novelty_HB_cols = DO_novelty_HB_cols[-1 * which(DO_novelty_HB_cols %in% c("HB_Mouse_ID","HB_date_of_test","HB_tester"))]

# Novel place preference
DO_novelty_NPP_cols = DO_novelty_cols[grep("^NPP_.*$",DO_novelty_cols)]
DO_novelty_NPP_cols = DO_novelty_NPP_cols[-1 * which(DO_novelty_NPP_cols %in% c("NPP_date_of_test","NPP_tester"))]

# Getting numeric columns
DO_novelty_numeric_cols = c(DO_novelty_OFA_cols, DO_novelty_LD_cols, DO_novelty_HB_cols, DO_novelty_NPP_cols)

DO_novelty_data_cols = DO_novelty_numeric_cols
```

Making data frame to carry novelty and IVSA data

```{r}
novelty_vars = c(DO_novelty_data_cols, "Group", "OFA_tester", "LD_tester",  "HB_tester")

# for raw data, group = dataset
nov_raw$dataset <- rep("precenter", nrow(nov_raw))
nov_raw$dataset[which(nov_raw$Group=="post_center")] <- "CSNA"
nov_raw$DE_Sex <- "F"
nov_raw$DE_Sex[which(nov_raw$Sex=="Male")] <- "M"

IVSA_vars = c(IVSA_data_vars, "AQ_SessionsToAcquisition")

DO_novelty_IVSA_IDs = intersect(row.names(DO_IVSA), row.names(DO_novelty))
# DE_Subject
DO_novelty_only_IDs <- setdiff(DO_novelty$Mouse_ID, row.names(DO_IVSA))

DO_novelty_IVSA = cbind(DO_IVSA[DO_novelty_IVSA_IDs,c(IVSA_DE_vars, IVSA_vars)],
                        DO_novelty[DO_novelty_IVSA_IDs,novelty_vars])

# Filtering for only animals that acquired IVSA or were acquisition-only.
DO_novelty_IVSA_raw = DO_novelty_IVSA

table(DO_novelty_IVSA$DE_Exit_Reason)
DO_novelty_IVSA = DO_novelty_IVSA[which(DO_novelty_IVSA$DE_Exit_Reason == "Finished Pipeline" |
                                          DO_novelty_IVSA$DE_Exit_Reason == "IVSA Acquisition Only"),]
```

Add in those that do not have IVSA data

```{r}
DO_novelty$DE_Subject = DO_novelty$Mouse_ID
DO_novelty$DE_Sex = gsub("^([FM])\\w+$","\\1",DO_novelty$Sex)
include <- DO_novelty[ which(DO_novelty$DE_Subject %in% DO_novelty_only_IDs), 
                                                   c("DE_Subject", "DE_Sex", novelty_vars)]
add <- which(!(colnames(DO_novelty_IVSA) %in% colnames(include)))
addto <- data.frame(array(NA, dim=c(nrow(include), length(add)), dimnames = list(NULL, colnames(DO_novelty_IVSA)[add])))
include <- cbind(DE_Subject=include$DE_Subject, DE_Sex=include$DE_Sex, addto, include[, -c(1,2)])

DO_novelty_IVSA <- rbind(DO_novelty_IVSA, include)
DO_novelty_IVSA$nov_only <- as.numeric(DO_novelty_IVSA$DE_Subject %in% DO_novelty_only_IDs)
DO_novelty_IVSA$dataset = ifelse(DO_novelty_IVSA$Group == "post_center","CSNA","precenter")
```

Look at the distribution of acquisition variables

For active lever presses, accounting for activity, use : DR_ALP_TfASoTD_1p0mgkg (Dose Response FR1-Active_LeverPresses_TotalForAllSessionsOnThisDose-1.0 mg/kg) divided by 
DR_ILP_TfASoTD_1p0mgkg (Dose Response FR1-InactiveLeverPresses_TotalForAllSessionsOnThisDose-1.0 mg/kg)

For mean amount of cocaine per session use: DR_Inf_TfASoTD_1p0mgkg: Dose Response FR1-Infusions_TotalForAllSessionsOnThisDose-1.0 mg/kg divided by the number of sessions

For consistency, use: DR_IEI_CoV_ALP_Total_1p0mgkg: Dose response FR1-InterEventInterval_CoefOfVariation_ActiveLeverPresses_Total-1.0 mg/kg

For rate of acquisition, use 1 - DO_novelty_IVSA$AQ_SessionsToAcquisition/28

```{r}
DO_novelty_IVSA$AQ_lever_ratio <- (DO_novelty_IVSA$DR_ALP_TfASoTD_1p0mgkg +1) / (DO_novelty_IVSA$DR_ILP_TfASoTD_1p0mgkg + 1)
DO_novelty_IVSA$AQ_mean_inf <- DO_novelty_IVSA$DR_Inf_TfASoTD_1p0mgkg / DO_novelty_IVSA$AQ_SessionsToAcquisition
DO_novelty_IVSA$AQ_active_CoV <- DO_novelty_IVSA$DR_IEI_CoV_ALP_Total_1p0mgkg
DO_novelty_IVSA$AQ_rate <- 1 - DO_novelty_IVSA$AQ_SessionsToAcquisition/28
ys <- c('AQ_lever_ratio', 'AQ_mean_inf', 'AQ_active_CoV', 'AQ_rate') 
summary(DO_novelty_IVSA[, ys])
#
summary(DO_novelty_IVSA$AQ_SessionsToAcquisition)
summary( DO_novelty_IVSA$DR_ALP_TfASoTD_1p0mgkg)
summary(DO_novelty_IVSA$DR_ILP_TfASoTD_1p0mgkg)
#
summary(DO_novelty_IVSA$AQ_rate)
#
DO_novelty_IVSA$AQ_rate[which( DO_novelty_IVSA$DR_ALP_TfASoTD_1p0mgkg == 0)]
DO_novelty_IVSA$AQ_rate[which( DO_novelty_IVSA$DR_ILP_TfASoTD_1p0mgkg == 0)]

# some mice have 0 active or 0 inactive lever presses --- should these be removed?
#
summary(DO_novelty_IVSA$DR_IEI_CoV_ALP_Total_1p0mgkg)
#

vars <- c(ys, 'dataset')
nas <- NULL
for (v in vars) {
  nas <- c(nas, which(is.na(DO_novelty_IVSA[, v])))
}
to_plot <- DO_novelty_IVSA[-nas, vars]
par(mfrow=c(2,2))
for (i in 1:length(ys)) {
  boxplot(to_plot[, ys[i]] ~ to_plot$dataset , xlab='dataset', ylab=ys[i])
}

```

Certainly there is confounding here. We should normalize separately and have 'precenter' in the model

```{r}
table(to_plot[, 'dataset'])
```


### Exclusions

Require they finish the pipeline and add include 'dataset' in the model.

```{r}
excluded <- intersect(which(DO_novelty_IVSA$nov_only==0), 
                      which(!(DO_novelty_IVSA$DE_Exit_Reason %in% c("Finished Pipeline", "IVSA Acquisition Only") &
                                !is.na(DO_novelty_IVSA$AQ_SessionsToAcquisition)))
)
print(paste0(length(excluded), " were excluded due to not finishing the pipeline."))
# df_all includes precenter data
df_all <- DO_novelty_IVSA[-excluded, ]
print(paste0(length(which(df_all$dataset=='precenter' & df_all$nov_only==0)), " were precenter."))
```

exclude NAs in the predictors

```{r}
#vars <- c(ys, novelty_vars[-which(novelty_vars=='dataset')], 'DE_Sex')
vars <- c(novelty_vars, 'DE_Sex')
vars <- vars[grep("tester", vars, invert = TRUE)]
vars <- vars[grep("_ranknorm$", vars, invert = TRUE)]
vars <- vars[grep("HB_Novel_Entries", vars, invert = TRUE)]
vars <- c(vars, "dataset")
nas <- NULL
n_nas <- rep(0, length(vars))
names(n_nas) <- vars
for (i in 1:length(vars)) {
  nas <- union(nas, which(is.na(df_all[, vars[i]])))
  n_nas[i] <- length(which(is.na(df_all[, vars[i]])))
}
print(paste0(length(nas), " were excluded do to missing data in the predictors. The dataset included ", nrow(df_all) - length(nas), " mice."))
```

### build the multivariate model

Elastic net is a predictive model that idenitfies which novelty variables are predictive and allows for highly correlated predictors.

### Elastic net

scale everything using rank Z normalization, separetely vy 'dataset'

```{r}
norm_rank_transform = function(x, c = 0) {
  stopifnot(is.numeric(x) & is.vector(x))
  x_noNA = which(!is.na(x))
  N = length(x_noNA)
  x[x_noNA] = qnorm((rank(x[x_noNA], ties.method = "average") - c) / (N - (2 * c) + 1))
  return(x)
}
```

Need to transform with everything in there, not just those we use to build the model

```{r}
vars <- c(vars, ys)
vars <- c(vars, colnames(df_all)[grepl("tester", colnames(df_all))])
dd <- df_all[ -nas, vars]
dd$HB_tester <- as.numeric(dd$HB_tester %in% c("TAR", "TRTW"))
dd$OFA_tester <- as.numeric(dd$OFA_tester %in% c("TAR", "TRTW"))
dd$LD_tester <- as.numeric(dd$LD_tester %in% c("TAR", "TRTW"))
#rownames(dd) <- rownames(y) <- df_all$DE_Subject[-nas]
rownames(dd) <- df_all$DE_Subject[-nas]
#
fvars <- c("DE_Sex", "dataset","HB_tester", "OFA_tester", "LD_tester","Group")
#
nvars <- setdiff(colnames(dd), fvars)
is.center <- which(dd$dataset=="CSNA")
x <- apply(dd[is.center, nvars], 2, norm_rank_transform)
is.pre <- setdiff(1:nrow(dd), is.center)
xx <- apply(dd[is.pre, nvars], 2, norm_rank_transform)
x <- rbind(x, xx)
#
rr <- cbind(rownames(x), rownames(dd))
all(rr[,1]==rr[,2])
idx <- match(rownames(x), rownames(dd))
rr <- cbind(rownames(x), rownames(dd)[idx])
all(rr[,1]==rr[,2])
dd <- dd[idx, ]
rr <- cbind(rownames(x), rownames(dd))
all(rr[,1]==rr[,2])
#
# it's in the right order now
#
```

```{r}
library(reshape2)
library(ggpubr)
##### plot the troyler effect after normalizing
is_set <- which(grepl("HB", colnames(x)))
dx <- data.frame(x[, is_set], dataset=dd$dataset, troyler=dd$HB_tester)
mm <- melt(dx, id.vars = c("dataset", "troyler"))
mm$troyler <- as.factor(mm$troyler)
jj <- length(is_set)
par(mfrow=c(1,jj))
gg <- ggplot(mm, aes(x=value))

gg1 <- gg+ geom_histogram(aes(color = dataset, fill = dataset, y = stat(width*density)),
                   position = "identity", bins=30, alpha=.3) +
  facet_wrap(~variable) + theme_bw() + 
  scale_color_manual(values=c("#d6604d", "#4393c3")) + 
  scale_fill_manual(values=c("#d6604d", "#4393c3")) +
  theme(strip.text.x = element_text(size = 4))

gg2 <- gg+ geom_histogram(aes(color = troyler, fill = troyler, y = stat(width*density)),
                   position = "identity", bins=30, alpha=.3) +
  facet_wrap(~variable) + theme_bw() +
  scale_color_manual(values=c("#9970ab", "#5aae61")) + 
  scale_fill_manual(values=c("#9970ab", "#5aae61")) +
  theme(strip.text.x = element_text(size = 4))
ggarrange(gg1, gg2,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
```

clearly something amiss with HB novel entries

```{r}
is_set <- which(grepl("LD", colnames(x)))
dx <- data.frame(x[, is_set], dataset=dd$dataset, troyler=dd$LD_tester)
mm <- melt(dx, id.vars = c("dataset", "troyler"))
mm$troyler <- as.factor(mm$troyler)
jj <- length(is_set)

gg <- ggplot(mm, aes(x=value))

gg1 <- gg+ geom_histogram(aes(color = dataset, fill = dataset, y = stat(width*density)),
                   position = "identity", bins=30, alpha=.3) +
  facet_wrap(~variable) + theme_bw() + 
  scale_color_manual(values=c("#d6604d", "#4393c3")) + 
  scale_fill_manual(values=c("#d6604d", "#4393c3"))+
  theme(strip.text.x = element_text(size = 4))

gg2 <- gg+ geom_histogram(aes(color = troyler, fill = troyler, y = stat(width*density)),
                   position = "identity", bins=30, alpha=.3) +
  facet_wrap(~variable) + theme_bw() +
  scale_color_manual(values=c("#9970ab", "#5aae61")) + 
  scale_fill_manual(values=c("#9970ab", "#5aae61")) +
  theme(strip.text.x = element_text(size = 4))
ggarrange(gg1, gg2,
                    labels = c("", ""),
                    ncol = 1, nrow = 2)
```

```{r}
is_set <- which(grepl("OFA", colnames(x)))
dx <- data.frame(x[, is_set], dataset=dd$dataset, troyler=dd$OFA_tester)
mm <- melt(dx, id.vars = c("dataset", "troyler"))
mm$troyler <- as.factor(mm$troyler)
jj <- length(is_set)

gg <- ggplot(mm, aes(x=value))

gg1 <- gg+ geom_histogram(aes(color = dataset, fill = dataset, y = stat(width*density)),
                   position = "identity", bins=30, alpha=.3) +
  facet_wrap(~variable) + theme_bw() + 
  scale_color_manual(values=c("#d6604d", "#4393c3")) + 
  scale_fill_manual(values=c("#d6604d", "#4393c3"))

gg2 <- gg+ geom_histogram(aes(color = troyler, fill = troyler, y = stat(width*density)),
                   position = "identity", bins=30, alpha=.3) +
  facet_wrap(~variable) + theme_bw() +
  scale_color_manual(values=c("#9970ab", "#5aae61")) + 
  scale_fill_manual(values=c("#9970ab", "#5aae61"))

print(gg1)
print(gg2)
# ggarrange(gg1, gg2,
#                     labels = c("", ""),
#                     ncol = 1, nrow = 2)
```

```{r}
for (i in 1:length(fvars)) {
  levels <- unique(dd[, fvars[i]])
  for (j in 1:length(levels)) {
    xx <- as.numeric(dd[, fvars[i]] == levels[j])
    x <- cbind(x, norm_rank_transform(xx))
    colnames(x)[ncol(x)] <- paste0(fvars[i], "=", levels[j])
  }
}
y <- as.matrix(x[, ys])
x <- as.matrix(x[, setdiff(colnames(x), ys)])
```

```{r}
no_y <- as.numeric(which(apply(y, 1, function(x) any(is.na(x)))))
x_all <- x; y_all <- y;
x <- x[-no_y, ]; y <- y[-no_y, ]
```

```{r}
alpha <- seq(0, 1, by=.1)
nfolds <- 5
set.seed(1216)
foldid=sample(1:nfolds, nrow(y), replace=TRUE)
```

```{r}
get_best <- function(x, y, alpha, family) {
  lmin <- best <- rep(NA, nfolds)
  cvfit <- list()
  for (i in 1:length(alpha)) {
    cvfit[[i]] <- cv.glmnet(x=x, y=y, alpha = alpha[i], 
                            family=family,
                            nfolds=nfolds, foldid=foldid) 
    lmin[i] <- cvfit[[i]]$lambda.min
    # cvm is the mean CV error (minimize this with lambda.min)
    best[i] <- min(cvfit[[i]]$cvm[which(cvfit[[i]]$lambda==lmin[i])])
  }
  is_best <- which.min(best)
  print(paste0("The best mean CV error was reached with alpha = ", alpha[is_best]))
  # pred <- predict(cvfit[[is_best]], s=lmin[is_best], type="response", newx=x)
  # boxplot(pred ~ y)
  if (family=="mgaussian") {
    res <- coef(cvfit[[is_best]], s=lmin[is_best])
    results <- NULL
    for (i in 1:length(res)) {
      results <- cbind(results, res[[i]][,1])
    }
    colnames(results) <- paste0("coef_", colnames(y))
  } else {
    results <- data.frame(coef=coef(cvfit[[is_best]], s=lmin[is_best])[,1])
    results$abs_coef <- abs(results[,1])
    results <- results[order(-results[, 2]), ]
    zs <- which(results[,1]==0)[1]
    if (!is.na(zs)) {
      results$rank <- NA
      results$rank[1:(zs-1)] <- 1:(zs-1)
    } else {
      results$rank <- 1:nrow(results)
    }
  }
  return(list(results=results, model=cvfit[[is_best]], lambda=lmin[is_best]))
}

```

```{r}
res <- get_best(x, y, alpha, family = "mgaussian")
results <- res$results
m <- res$model
lmin <- res$lambda
```
nearly a ridge regression

```{r}
plot(m)
```

this is the cross-validation results across a range of lambda. We choose the lambda that yields the lowest MSE (lambda.min).

```{r}
results
```


```{r}
results <- as.data.frame(results)
minmax <- c(min(results), max(results))
column=1
#plot_coef <- function(column, results=results, minmax=minmax) {
  notit <- setdiff(1:ncol(results), column)
  par(mfrow=c(1, length(notit)))
  for (i in 1:length(notit)) {
    plot(results[, column], results[, notit[i]], xlab=colnames(results)[column], ylab=colnames(results)[notit[i]],
         xlim=minmax, ylim=minmax)
  }
#}
```

```{r}
column=2
#plot_coef <- function(column, results=results, minmax=minmax) {
  notit <- setdiff(1:ncol(results), column)
  par(mfrow=c(1, length(notit)))
  for (i in 1:length(notit)) {
    plot(results[, column], results[, notit[i]], xlab=colnames(results)[column], ylab=colnames(results)[notit[i]],
         xlim=minmax, ylim=minmax)
  }
```

```{r}
column=3
#plot_coef <- function(column, results=results, minmax=minmax) {
  notit <- setdiff(1:ncol(results), column)
  par(mfrow=c(1, length(notit)))
  for (i in 1:length(notit)) {
    plot(results[, column], results[, notit[i]], xlab=colnames(results)[column], ylab=colnames(results)[notit[i]],
         xlim=minmax, ylim=minmax)
  }
```

```{r}
column=4
#plot_coef <- function(column, results=results, minmax=minmax) {
  notit <- setdiff(1:ncol(results), column)
  par(mfrow=c(1, length(notit)))
  for (i in 1:length(notit)) {
    plot(results[, column], results[, notit[i]], xlab=colnames(results)[column], ylab=colnames(results)[notit[i]],
         xlim=minmax, ylim=minmax)
  }
```

from these plots, we can see that the coefficients for the ratio of active to inactive lever presses are a bit noisier than the other measures of acquisition coefficients but they all correlate well with one another. The coefficient of variation coefficients correlate very well with mean infusion and rate of acquistion.

```{r}
for (i in 1:ncol(results)) {
  ac <- data.frame(abs_coef=abs(results[, i]), rank=rep(0, nrow(results)))
  rownames(ac) <- rownames(results)
  ac <- ac[order(-ac$abs_coef), ]
  ac$rank <- 1:nrow(results)
  idx <- match(rownames(results), rownames(ac))
  results <- cbind(results, ac$rank[idx])
}
colnames(results)[(i+1):ncol(results)] <- paste0("rank_", colnames(y))
results <- results[order(results$rank_AQ_active_CoV, results$rank_AQ_lever_ratio, results$rank_AQ_mean_inf, results$coef_AQ_rate), ]
results$median_rank <- apply(results[, 5:8], 1, median)
results <- results[order(results$median_rank), ]
results
#write.csv(results, "./data/20_elastic_mv_results.csv")
```

### figures

```{r}
require(reshape2)
results$pred <- rownames(results)
rr <- max(results$median_rank[which(abs(results$coef_AQ_lever_ratio) > 0)])
cc <- results[which(results$median_rank <= rr), 1:4]
#cc$rank <- results$median_rank
cc$pred <- rownames(cc)
mm <- melt(cc, id.vars = 'pred')
```

```{r}
library(RColorBrewer)
cols <- brewer.pal(4, "Paired")
gg <- ggplot(mm, aes(x = value, y=reorder(pred, abs(value)), colour=variable)) + geom_point(size=2) 
gg + theme_bw() + geom_vline(xintercept =0) + xlim(-max(minmax), max(minmax)) + 
  xlab("standardized coefficient") + ylab("") + labs(colour="Acquistion measure") +
  scale_fill_manual(values = cols, aesthetics=c('colour'), labels = c("Active/inactive presses", "Mean cocaine infusion", "CoV active presses", "Rate of acquisition")) + theme(legend.position=c(-.05,1.05), legend.background=element_blank(),
                                                                                                                                                                                legend.direction = "horizontal", legend.title = element_blank(), plot.margin = unit(c(1,1,1,1), "cm"))
  #theme(legend.position = "top", legend.title = element_blank(), legend.)
```

```{r}
ggout <- gg + theme_bw() + geom_vline(xintercept =0) + xlim(-max(minmax), max(minmax)) + 
  xlab("standardized coefficient") + ylab("") + labs(colour="Acquistion measure") +
  scale_fill_manual(values = cols, aesthetics=c('colour'), labels = c("Active/inactive presses", "Mean cocaine infusion", "CoV active presses", "Rate of acquisition")) + theme(legend.position=c(-.05,1.05), legend.background=element_blank(),
                                                                                                                                                                                legend.direction = "horizontal", legend.title = element_blank(), plot.margin = unit(c(1,1,1,1), "cm"))
ggout
fn <- paste0("./data/figures/20_elasticnet_coef.png")
png(fn, res=200, height = 5, width = 7, units = "in")
print(ggout)
dev.off()
```

# Predict on all data

```{r}
pred <- predict(m, newx=x_all, s="lambda.min", gamma="gamma.min", type="response")
out <- data.frame(DE_Subject=rownames(pred), 
                  in_model=as.numeric(rownames(pred) %in% rownames(y)), pred[,,1])
saveRDS(out, file="./data/20_elasticnet_predictions.RDS")
```

