---
title: "DO Cocaine and Saline Sensitization Canonical Correlations"
author: "Michael C. Saul (michael.saul [at] jax.org)"
output: workflowr::wflow_html
---

# Background

## Motivation

### Purpose of analysis

This analysis is performed to process the novelty data, sensitization saline data, and sensitization cocaine data.
2) Strain-by-sex means and standard errors for plotting

**These data were collected by the CSNA behavioral phenotyping core.**

# Analysis

## Setup

### R libraries

Calling R libraries necessary for this analysis.

```{r warning=FALSE, message=FALSE}
library("dplyr")
library("tidyr")
library("tidyverse")
library("lubridate")
library("ggplot2")
library("cowplot")
library("MASS")
library("ggbeeswarm")
```

### Current Date

Getting current date

```{r}
current_date = format(Sys.time(),"%Y-%m-%d")
current_date
```

## Importing data

### Getting MPD Site Information

Currently using internal access to the JAX MPD curation site.

```{r mpd_old_prefix, eval=FALSE}
MPD_prefix = "http://mpdcuration.jax.org:82/api/pheno/animalvals/"
MPD_suffix = "?csv=yes"
```

### Importing raw saline and cocaine response data from MPD

First, getting table of saline and cocaine measures in MPD

```{r}
saline_cocaine_measures = read.table("./data/mpd_measures_saline_cocaine.txt",
                                     header = TRUE, sep = "\t")
# filtering to only post-injection data
saline_measures_post = saline_cocaine_measures[which(saline_cocaine_measures$injection_time == "post" &
                                                     saline_cocaine_measures$saline_cocaine == "saline"),]
cocaine_measures_post = saline_cocaine_measures[which(saline_cocaine_measures$injection_time == "post" &
                                                      saline_cocaine_measures$saline_cocaine == "cocaine"),]
```

Next, getting cocaine and saline datasets from MPD.

```{r new_mpd}
# Getting a base for the MPD measures
mpd_series_base = "https://phenome.jax.org/api/pheno/animalvals/series/MEASURE?csv=1"

# Getting cocaine sensitization MPD measures IDs
cocaine_sensi_measures = c("90309","90315","90321","90327",
                           "90442","90333","90387")
cocaine_sensi_colnames = c("animal_id", cocaine_measures_post$measure)

# Getting saline sensitization MPD measures IDs
saline_sensi_measures = c("90306","90312","90318","90324",
                          "90439","90330","90384")
saline_sensi_colnames = c("animal_id", saline_measures_post$measure)

# Pulling data from MPD for cocaine locomotor sensitization
for (i in seq_len(length(cocaine_sensi_measures))) {
  mpd_csv_i = gsub("MEASURE", cocaine_sensi_measures[i], mpd_series_base)
  mpd_table_i = read_csv(mpd_csv_i)
  if (i == 1) {
    mpd_cocaine_table_long = mpd_table_i
  } else {
    mpd_cocaine_table_long = rbind(mpd_cocaine_table_long, mpd_table_i)
  }
}

# Getting cocaine measure names
cocaine_measure_names = unique(pull(mpd_cocaine_table_long, varname))

# Making a wide format table for cocaine measures
mpd_cocaine_sensi_table = mpd_cocaine_table_long |>
  pivot_wider(id_cols = c(animal_id, animal_projid, strain,
                          sex, stocknum, strainid),
              names_from = varname,
              values_from = value) |>
  filter(strain == "J:DO") |>
  as.data.frame()
row.names(mpd_cocaine_sensi_table) = mpd_cocaine_sensi_table$animal_id
cocaine_measures_data = mpd_cocaine_sensi_table[,cocaine_sensi_colnames]

# Pulling data from MPD for saline locomotor sensitization
for (i in seq_len(length(saline_sensi_measures))) {
  mpd_csv_i = gsub("MEASURE", saline_sensi_measures[i], mpd_series_base)
  mpd_table_i = read_csv(mpd_csv_i)
  if (i == 1) {
    mpd_saline_table_long = mpd_table_i
  } else {
    mpd_saline_table_long = rbind(mpd_saline_table_long, mpd_table_i)
  }
}

# Getting saline measure names
saline_measure_names = unique(pull(mpd_saline_table_long, varname))

# Making a wide format table for saline measures
mpd_saline_sensi_table = mpd_saline_table_long |>
  pivot_wider(id_cols = c(animal_id, animal_projid, strain,
                          sex, stocknum, strainid),
              names_from = varname,
              values_from = value) |>
  filter(strain == "J:DO") |>
  as.data.frame()
row.names(mpd_saline_sensi_table) = mpd_saline_sensi_table$animal_id
saline_measures_data = mpd_saline_sensi_table[,saline_sensi_colnames]
```

### Importing novelty response data

Loading novelty response data and preparing for RTA.

```{r}
DO_novelty_response = readRDS("./data/DO_novelty_response_data.RDS")
DO_novelty_response$Sex = gsub("^([MF])\\w+$","\\1",DO_novelty_response$Sex)
DO_saline_novelty = DO_novelty_response[row.names(saline_measures_data),]
DO_saline_novelty = cbind(DO_saline_novelty, saline_measures_data[,-1])
DO_cocaine_novelty = DO_novelty_response[row.names(cocaine_measures_data),]
DO_cocaine_novelty = cbind(DO_cocaine_novelty, cocaine_measures_data[,-1])

# Getting columns of each type of measure
saline_columns = colnames(saline_measures_data[,-1])
cocaine_columns = colnames(cocaine_measures_data[,-1])
novelty_columns = colnames(DO_novelty_response)
novelty_columns = novelty_columns[grep("batch_ranknorm$",novelty_columns)]
```

### Saline RTA

```{r}
# Getting highest correlation variables to start out
highest_cor = cor(DO_saline_novelty[,"dist_d3_d11_auc_cont_do"], 
                  DO_saline_novelty[,novelty_columns],
                  use = "pairwise.complete.obs")
highest_cor_r = max(abs(highest_cor))
highest_cor_ind = which(abs(highest_cor) == highest_cor_r, arr.ind = TRUE)
saline_highcor_id = "dist_d3_d11_auc_cont_do"
novelty_highcor_id = colnames(highest_cor)[highest_cor_ind[1,"col"]]

paste0("The highest correlation (", round(highest_cor_r, 2),") is between ", saline_highcor_id, " and ",
       novelty_highcor_id, ".")
```

Running canonical correlation on saline-treated animals

```{r}
# Starting with these as best novelty and IVSA variables
best_novelty_vars = novelty_highcor_id
best_saline_vars = saline_highcor_id
noNA_rows = which(rowSums(is.na(DO_saline_novelty[,c(best_novelty_vars, best_saline_vars)])) == 0)
starting_cancor =  stats::cancor(DO_saline_novelty[noNA_rows,best_novelty_vars], 
                                 DO_saline_novelty[noNA_rows,best_saline_vars],
                                 xcenter = TRUE, ycenter = TRUE)

# Selecting appropriate saline variables
saline_vars_unselected = c("dist_d3_d2_cont_do","dist_d5_d3_cont_do","dist_d12_d2_cont_do","dist_d19_d11_cont_do")
novelty_vars_unselected = novelty_columns[(-1 * which(novelty_columns == best_novelty_vars))]


not_optimized = TRUE
min_obs = 225
max_var = 10

while (not_optimized) {
  best_cancor = starting_cancor$cor[1]
  best_var = ""
  best_paradigm = ""
  
  for (i in novelty_vars_unselected) {
    noNA_rows = which(rowSums(is.na(DO_saline_novelty[,c(best_novelty_vars, i, best_saline_vars)])) == 0)
    if (length(noNA_rows) >= min_obs) {
      cancor_i = stats::cancor(DO_saline_novelty[noNA_rows, c(best_novelty_vars, i)], DO_saline_novelty[noNA_rows, best_saline_vars],
                        xcenter = TRUE, ycenter = TRUE)
      if (cancor_i$cor[1] > best_cancor) {
        best_cancor = cancor_i$cor[1]
        best_var = i
        best_paradigm = "novelty"
      }
    }
  }
  
  for (j in saline_vars_unselected) {
    noNA_rows = which(rowSums(is.na(DO_saline_novelty[,c(best_novelty_vars, j, best_saline_vars)])) == 0)
    if (length(noNA_rows) >= min_obs) {
      cancor_j = stats::cancor(DO_saline_novelty[noNA_rows, best_novelty_vars], DO_saline_novelty[noNA_rows,c(best_saline_vars, j)],
                        xcenter = TRUE, ycenter = TRUE)
      if (cancor_j$cor[1] > best_cancor) {
        best_cancor = cancor_j$cor[1]
        best_var = j
        best_paradigm = "saline"
      }
    }
  }
  
  if (best_paradigm == "novelty") {
    novelty_vars_test = c(best_novelty_vars, best_var)
    saline_vars_test = best_saline_vars
  } else if (best_paradigm == "saline") {
    novelty_vars_test = best_novelty_vars
    saline_vars_test = c(best_saline_vars, best_var)
  }
  
  noNA_rows = which(rowSums(is.na(DO_saline_novelty[,c(novelty_vars_test, saline_vars_test)])) == 0)
  k_gtr = c()
  
  B = 1e4
  for (k in 1:B) {
    cancor_k =  stats::cancor(DO_saline_novelty[sample(noNA_rows), novelty_vars_test], 
                      DO_saline_novelty[noNA_rows, saline_vars_test],
                      xcenter = TRUE, ycenter = TRUE)
    k_gtr = c(k_gtr, cancor_k$cor[1])
  }
  p_value_improvement = (length(which(k_gtr > best_cancor)) + 1) / (B + 1)
  
  if ((length(best_novelty_vars) + length(best_saline_vars)) > max_var) {
    not_optimized = FALSE
  } else if (p_value_improvement < 0.001) {
    if (best_paradigm == "novelty") {
      best_novelty_vars = c(best_novelty_vars, best_var)
      novelty_vars_unselected = novelty_vars_unselected[-1 * which(novelty_vars_unselected == best_var)]
    } else if (best_paradigm == "saline") {
      best_saline_vars = c(best_saline_vars, best_var)
      saline_vars_unselected = saline_vars_unselected[-1 * which(saline_vars_unselected == best_var)]
    }
    starting_cancor =  stats::cancor(DO_saline_novelty[noNA_rows,best_novelty_vars], DO_saline_novelty[noNA_rows,best_saline_vars],
                             xcenter = TRUE, ycenter = TRUE)
  } else {
    not_optimized = FALSE
  }
}
noNA_rows = which(rowSums(is.na(DO_saline_novelty[,c(best_novelty_vars, best_saline_vars)])) == 0)

cat("Best novelty variables:\n", paste(best_novelty_vars, sep = "", collapse = "\n"),"\n\n", sep = "")
cat("Best saline variables:\n", paste(best_saline_vars, sep = "", collapse = "\n"), "\n\n", sep = "")
cat("First canonical correlate magnitude: ", round(starting_cancor$cor[1], 4), "\n\n", sep = "")
cat("Canonical correlation trained on ", length(noNA_rows), " complete observations.", sep = "")
```

Adjusting this canonical correlation for sex.

```{r}
DO_saline_novelty$DE_Sex = DO_saline_novelty$Sex
DO_saline_novelty$Sex = ifelse(DO_saline_novelty$DE_Sex == "M", 1, 0)
novelty_cancor_vars_SAL = c(best_novelty_vars,"Sex")
saline_cancor_vars_SAL = c(best_saline_vars,"Sex")

saline_cancor_rows_SAL = which(rowSums(is.na(DO_saline_novelty[,c(novelty_cancor_vars_SAL,saline_cancor_vars_SAL)])) == 0)

saline_novelty_cancor_SAL =  stats::cancor(DO_saline_novelty[saline_cancor_rows_SAL,saline_cancor_vars_SAL],
                                 DO_saline_novelty[saline_cancor_rows_SAL,novelty_cancor_vars_SAL],
                                 xcenter = TRUE, ycenter = TRUE)
paste("The first canonical correlate of these saline variables to novelty variables has a magnitude of ", 
      round(saline_novelty_cancor_SAL$cor[2], digits = 3), 
      ".", sep = "")
paste("This canonical correlation is based upon ",
      length(saline_cancor_rows_SAL), " complete observations.", sep = "")
```

This is an adequate fit for the canonical correlation. Plotting the variables.

```{r}
source("./code/ggplot_pub_themes.R")

saline_cancor = as.matrix(DO_saline_novelty[saline_cancor_rows_SAL,saline_cancor_vars_SAL]) %*% saline_novelty_cancor_SAL$xcoef[,2]
novelty_cancor = as.matrix(DO_saline_novelty[saline_cancor_rows_SAL,novelty_cancor_vars_SAL]) %*% saline_novelty_cancor_SAL$ycoef[,2]

saline_novelty_cancor_SAL_df = data.frame(saline_cancor = saline_cancor, novelty_cancor = novelty_cancor)
saline_novelty_cancor_SAL_df$Sex = DO_saline_novelty[row.names(saline_novelty_cancor_SAL_df),"DE_Sex"]
saline_novelty_cancor_SAL_df$Subject = as.numeric(as.character(row.names(saline_novelty_cancor_SAL_df)))
saline_novelty_cancor_SAL_df$Acquired = DO_saline_novelty[row.names(saline_novelty_cancor_SAL_df),"DE_Exit_Reason"]
saline_novelty_cancor_lm = lm(saline_cancor ~ novelty_cancor, data = saline_novelty_cancor_SAL_df)
novelty_saline_SAL_cancor_plot = ggplot(data = saline_novelty_cancor_SAL_df, aes(x = novelty_cancor, y = saline_cancor, color = Sex)) +
  geom_point(size = (pt_to_mm * 1.5)) +
  geom_abline(slope = saline_novelty_cancor_lm$coefficients["novelty_cancor"], 
              intercept = saline_novelty_cancor_lm$coefficients["(Intercept)"],
              size = (1 * pt_to_mm)) +
  scale_color_manual(values = c("#3399CC","#66CC66")) +
  xlab("Novelty Canonical Correlate") +
  ylab("Saline Canonical Correlate")
novelty_saline_SAL_cancor_plot + theme_bw() + theme(panel.grid = element_line(color = "#FFFFFF"))
```

### Cocaine RTA

```{r}
# Getting highest correlation variables to start out
highest_cor = cor(DO_cocaine_novelty[,"dist_d3_d11_auc_cocaine_do"], 
                  DO_cocaine_novelty[,novelty_columns],
                  use = "pairwise.complete.obs")
highest_cor_r = max(abs(highest_cor))
highest_cor_ind = which(abs(highest_cor) == highest_cor_r, arr.ind = TRUE)
cocaine_highcor_id = "dist_d3_d11_auc_cocaine_do"
novelty_highcor_id = colnames(highest_cor)[highest_cor_ind[1,"col"]]

paste0("The highest correlation (", round(highest_cor_r, 2),") is between ", cocaine_highcor_id, " and ",
       novelty_highcor_id, ".")
```

Running canonical correlation on cocaine-treated animals

```{r}
# Starting with these as best novelty and IVSA variables
best_novelty_vars = novelty_highcor_id
best_cocaine_vars = cocaine_highcor_id
noNA_rows = which(rowSums(is.na(DO_cocaine_novelty[,c(best_novelty_vars, best_cocaine_vars)])) == 0)
starting_cancor =  stats::cancor(DO_cocaine_novelty[noNA_rows,best_novelty_vars], 
                                 DO_cocaine_novelty[noNA_rows,best_cocaine_vars],
                                 xcenter = TRUE, ycenter = TRUE)

# Selecting cocaine sensi variables
cocaine_vars_unselected = c("dist_d3_d2_cocaine_do","dist_d5_d3_cocaine_do","dist_d12_d2_cocaine_do","dist_d19_d11_cocaine_do")
novelty_vars_unselected = novelty_columns[(-1 * which(novelty_columns == best_novelty_vars))]

not_optimized = TRUE
min_obs = 225
max_var = 10

while (not_optimized) {
  best_cancor = starting_cancor$cor[1]
  best_var = ""
  best_paradigm = ""
  
  for (i in novelty_vars_unselected) {
    noNA_rows = which(rowSums(is.na(DO_cocaine_novelty[,c(best_novelty_vars, i, best_cocaine_vars)])) == 0)
    if (length(noNA_rows) >= min_obs) {
      cancor_i = stats::cancor(DO_cocaine_novelty[noNA_rows, c(best_novelty_vars, i)], DO_cocaine_novelty[noNA_rows, best_cocaine_vars],
                        xcenter = TRUE, ycenter = TRUE)
      if (cancor_i$cor[1] > best_cancor) {
        best_cancor = cancor_i$cor[1]
        best_var = i
        best_paradigm = "novelty"
      }
    }
  }
  
  for (j in cocaine_vars_unselected) {
    noNA_rows = which(rowSums(is.na(DO_cocaine_novelty[,c(best_novelty_vars, j, best_cocaine_vars)])) == 0)
    if (length(noNA_rows) >= min_obs) {
      cancor_j = stats::cancor(DO_cocaine_novelty[noNA_rows, best_novelty_vars], DO_cocaine_novelty[noNA_rows,c(best_cocaine_vars, j)],
                        xcenter = TRUE, ycenter = TRUE)
      if (cancor_j$cor[1] > best_cancor) {
        best_cancor = cancor_j$cor[1]
        best_var = j
        best_paradigm = "cocaine"
      }
    }
  }
  
  if (best_paradigm == "novelty") {
    novelty_vars_test = c(best_novelty_vars, best_var)
    cocaine_vars_test = best_cocaine_vars
  } else if (best_paradigm == "cocaine") {
    novelty_vars_test = best_novelty_vars
    cocaine_vars_test = c(best_cocaine_vars, best_var)
  }
  
  noNA_rows = which(rowSums(is.na(DO_cocaine_novelty[,c(novelty_vars_test, cocaine_vars_test)])) == 0)
  k_gtr = c()
  
  B = 1e4
  for (k in 1:B) {
    cancor_k =  stats::cancor(DO_cocaine_novelty[sample(noNA_rows), novelty_vars_test], 
                      DO_cocaine_novelty[noNA_rows, cocaine_vars_test],
                      xcenter = TRUE, ycenter = TRUE)
    k_gtr = c(k_gtr, cancor_k$cor[1])
  }
  p_value_improvement = (length(which(k_gtr > best_cancor)) + 1) / (B + 1)
  
  if ((length(best_novelty_vars) + length(best_cocaine_vars)) > max_var) {
    not_optimized = FALSE
  } else if (p_value_improvement < 0.001) {
    if (best_paradigm == "novelty") {
      best_novelty_vars = c(best_novelty_vars, best_var)
      novelty_vars_unselected = novelty_vars_unselected[-1 * which(novelty_vars_unselected == best_var)]
    } else if (best_paradigm == "cocaine") {
      best_cocaine_vars = c(best_cocaine_vars, best_var)
      cocaine_vars_unselected = cocaine_vars_unselected[-1 * which(cocaine_vars_unselected == best_var)]
    }
    starting_cancor =  stats::cancor(DO_cocaine_novelty[noNA_rows,best_novelty_vars], DO_cocaine_novelty[noNA_rows,best_cocaine_vars],
                             xcenter = TRUE, ycenter = TRUE)
  } else {
    not_optimized = FALSE
  }
}
noNA_rows = which(rowSums(is.na(DO_cocaine_novelty[,c(best_novelty_vars, best_cocaine_vars)])) == 0)

cat("Best novelty variables:\n", paste(best_novelty_vars, sep = "", collapse = "\n"),"\n\n", sep = "")
cat("Best cocaine variables:\n", paste(best_cocaine_vars, sep = "", collapse = "\n"), "\n\n", sep = "")
cat("First canonical correlate magnitude: ", round(starting_cancor$cor[1], 4), "\n\n", sep = "")
cat("Canonical correlation trained on ", length(noNA_rows), " complete observations.", sep = "")
```

Adjusting this canonical correlation for sex.

```{r}
DO_cocaine_novelty$DE_Sex = DO_cocaine_novelty$Sex
DO_cocaine_novelty$Sex = ifelse(DO_cocaine_novelty$DE_Sex == "M", 1, 0)
novelty_cancor_vars_COC = c(best_novelty_vars,"Sex")
cocaine_cancor_vars_COC = c(best_cocaine_vars,"Sex")

cocaine_cancor_rows_COC = which(rowSums(is.na(DO_cocaine_novelty[,c(novelty_cancor_vars_COC,cocaine_cancor_vars_COC)])) == 0)

cocaine_novelty_cancor_COC =  stats::cancor(DO_cocaine_novelty[cocaine_cancor_rows_COC,cocaine_cancor_vars_COC],
                                 DO_cocaine_novelty[cocaine_cancor_rows_COC,novelty_cancor_vars_COC],
                                 xcenter = TRUE, ycenter = TRUE)
paste("The first canonical correlate of these cocaine variables to novelty variables has a magnitude of ", 
      round(cocaine_novelty_cancor_COC$cor[2], digits = 3), 
      ".", sep = "")
paste("This canonical correlation is based upon ",
      length(cocaine_cancor_rows_COC), " complete observations.", sep = "")
```

This is an adequate fit for the canonical correlation. Plotting the variables.

```{r}
source("./code/ggplot_pub_themes.R")

cocaine_cancor = as.matrix(DO_cocaine_novelty[cocaine_cancor_rows_COC,cocaine_cancor_vars_COC]) %*% cocaine_novelty_cancor_COC$xcoef[,2]
novelty_cancor = as.matrix(DO_cocaine_novelty[cocaine_cancor_rows_COC,novelty_cancor_vars_COC]) %*% cocaine_novelty_cancor_COC$ycoef[,2]

cocaine_novelty_cancor_COC_df = data.frame(cocaine_cancor = cocaine_cancor, novelty_cancor = novelty_cancor)
cocaine_novelty_cancor_COC_df$Sex = DO_cocaine_novelty[row.names(cocaine_novelty_cancor_COC_df),"DE_Sex"]
cocaine_novelty_cancor_COC_df$Subject = as.numeric(as.character(row.names(cocaine_novelty_cancor_COC_df)))
cocaine_novelty_cancor_COC_df$Acquired = DO_cocaine_novelty[row.names(cocaine_novelty_cancor_COC_df),"DE_Exit_Reason"]
cocaine_novelty_cancor_lm = lm(cocaine_cancor ~ novelty_cancor, data = cocaine_novelty_cancor_COC_df)
novelty_cocaine_COC_cancor_plot = ggplot(data = cocaine_novelty_cancor_COC_df, aes(x = novelty_cancor, y = cocaine_cancor, color = Sex)) +
  geom_point(size = (pt_to_mm * 1.5)) +
  geom_abline(slope = cocaine_novelty_cancor_lm$coefficients["novelty_cancor"], 
              intercept = cocaine_novelty_cancor_lm$coefficients["(Intercept)"],
              size = (1 * pt_to_mm)) +
  scale_color_manual(values = c("#3399CC","#66CC66")) +
  xlab("Novelty Canonical Correlate") +
  ylab("Cocaine Sensitization Canonical Correlate")
novelty_cocaine_COC_cancor_plot + theme_bw() + theme(panel.grid = element_line(color = "#FFFFFF"))
```


### Making Predictions

Generating predicted variables from these data.

```{r}
DO_novelty = DO_novelty_response
DO_novelty$Sex = ifelse(DO_novelty$Sex == "M", 1, 0)

# saline
DO_predict_rows_SAL = row.names(DO_novelty)[which(rowSums(is.na(DO_novelty[,novelty_cancor_vars_SAL])) == 0)]
saline_prediction_SAL = as.numeric(as.matrix(DO_novelty[DO_predict_rows_SAL,novelty_cancor_vars_SAL]) %*% saline_novelty_cancor_SAL$ycoef[,2])
names(saline_prediction_SAL) = DO_predict_rows_SAL

# cocaine
DO_predict_rows_COC = row.names(DO_novelty)[which(rowSums(is.na(DO_novelty[,novelty_cancor_vars_COC])) == 0)]
cocaine_prediction_COC = as.numeric(as.matrix(DO_novelty[DO_predict_rows_COC,novelty_cancor_vars_COC]) %*% cocaine_novelty_cancor_COC$ycoef[,2])
names(cocaine_prediction_COC) = DO_predict_rows_COC

# union
DO_predict_rows_ALL = unique(c(DO_predict_rows_SAL, DO_predict_rows_COC))

saline_cocaine_pred = data.frame(row.names = DO_predict_rows_ALL,
                                 Mouse_ID = DO_predict_rows_ALL,
                                 Sex = DO_novelty[DO_predict_rows_ALL,"Sex"],
                                 Generation = DO_novelty[DO_predict_rows_ALL,"Generation"],
                                 saline_novelty_cancor = saline_prediction_SAL[DO_predict_rows_ALL],
                                 cocaine_novelty_cancor = cocaine_prediction_COC[DO_predict_rows_ALL],
                                 stringsAsFactors = FALSE)

today = as.character(lubridate::today())
saveRDS(saline_cocaine_pred, paste0("./data/DO_novelty_saline_cocaine_cancor_",today,".RDS"))
saveRDS(cocaine_novelty_cancor_COC, paste0("./data/DO_novelty_COC_cancor_",today,".RDS"))
saveRDS(saline_novelty_cancor_SAL, paste0("./data/DO_novelty_SAL_cancor_",today,".RDS"))
```

### R session and OS information

```{r sessionInfo}
novelty_saline_cancor_sessionInfo = sessionInfo()
novelty_saline_cancor_sessionInfo
```

## Document Control

This document was prepared using RMarkdown in RStudio.
