---
title: "DO IVSA, Saline, and Cocaine Sensitization Trait Correlation Figures"
author: "Michael C. Saul (michael.saul [at] jax.org)"
output: workflowr::wflow_html
---

# Background

## Motivation

### Purpose of analysis

This script is used to correlate traits in the IVSA assay. The specific traits correlated are the ones derived from the canonical correlation analysis.

# Analysis

## Setup

### R libraries

Calling R libraries necessary for this analysis.

```{r}
library("corrplot")
```

### Getting `norm_rank_transform` function

```{r}
norm_rank_transform = function(x, c = (0)) {
  stopifnot(is.numeric(x) & is.vector(x))
  N = length(x)
  return(qnorm((rank(x) - c) / (N - (2 * c) + 1)))
}
```

### Importing data

```{r}
DO_RTG_analysis_2 = readRDS("./data/DO_IVSA_prediction_a2_AQ_cancor.RDS")
DO_RTG_analysis_3 = readRDS("./data/DO_IVSA_prediction_a3_ALL_cancor.RDS")

# Loading behavioral data frames
DO_novelty_response_raw = readRDS("./data/DO_novelty_response_data.RDS")
DO_IVSA = readRDS("./data/DO_IVSA_data.RDS")
DO_cocaine_sensi = readRDS("./data/DO_cocaine_measures_data.RDS")
DO_saline_sensi = readRDS("./data/DO_saline_measures_data.RDS")

# Loading canonical correlations
IVSA_novelty_cancor_AQ = readRDS("./data/DO_IVSA_novelty_cancor_AQ.RDS")
IVSA_novelty_cancor_ALL = readRDS("./data/DO_IVSA_novelty_cancor_ALL.RDS")
cocaine_novelty_cancor_COC = readRDS("./data/DO_novelty_COC_cancor.RDS")
saline_novelty_cancor_SAL = readRDS("./data/DO_novelty_SAL_cancor.RDS")
```

### Making IVSA corrplot

```{r}
IVSA_cancor_vars = unique(c(names(IVSA_novelty_cancor_ALL$xcenter),
                            names(IVSA_novelty_cancor_AQ$xcenter)))
IVSA_cancor_vars = IVSA_cancor_vars[grep("Sex",IVSA_cancor_vars,invert=TRUE)]
IVSA_corrmatrix = cor(DO_IVSA[,IVSA_cancor_vars],
                 use = "pairwise.complete.obs")
colnames(IVSA_corrmatrix) = gsub("_batch_ranknorm$","",colnames(IVSA_corrmatrix))
row.names(IVSA_corrmatrix) = gsub("_batch_ranknorm$","",row.names(IVSA_corrmatrix))
corrplot(IVSA_corrmatrix, order = "hclust", hclust.method = "ward.D")
```

### Making sensitization corrplots

```{r}
SENSI_cocaine_cancor_vars = names(cocaine_novelty_cancor_COC$xcenter)
SENSI_cocaine_cancor_vars = SENSI_cocaine_cancor_vars[grep("Sex",SENSI_cocaine_cancor_vars,invert=TRUE)]
SENSI_COC_corrmatrix = cor(DO_cocaine_sensi[,SENSI_cocaine_cancor_vars],
                 use = "pairwise.complete.obs")
colnames(SENSI_COC_corrmatrix) = gsub("_batch_ranknorm$","",colnames(SENSI_COC_corrmatrix))
row.names(SENSI_COC_corrmatrix) = gsub("_batch_ranknorm$","",row.names(SENSI_COC_corrmatrix))
corrplot(SENSI_COC_corrmatrix, order = "hclust", hclust.method = "ward.D")
```

```{r}
SENSI_saline_cancor_vars = names(saline_novelty_cancor_SAL$xcenter)
SENSI_saline_cancor_vars = SENSI_saline_cancor_vars[grep("Sex",SENSI_saline_cancor_vars,invert=TRUE)]
SENSI_SAL_corrmatrix = cor(DO_saline_sensi[,SENSI_saline_cancor_vars],
                           use = "pairwise.complete.obs")
colnames(SENSI_SAL_corrmatrix) = gsub("_batch_ranknorm$","",colnames(SENSI_SAL_corrmatrix))
row.names(SENSI_SAL_corrmatrix) = gsub("_batch_ranknorm$","",row.names(SENSI_SAL_corrmatrix))
corrplot(SENSI_SAL_corrmatrix, order = "hclust", hclust.method = "ward.D")
```

### Saving output

```{r}
# saveRDS(corrplot,"./data/figures/DO_IVSA_behaviors_corrplot.RDS")
saveRDS(IVSA_corrmatrix,"./data/figures/DO_IVSA_behaviors_corrplot_data.RDS")
```

### Document Control

This document was prepared using RMarkdown in RStudio.
